---
title: "Useful EDA"
author: "Belle Schmidt"
date: "2024-07-02"
output: html_document
---


### Libraries

```{r}
library(tidyverse)
library(ggridges)
library(ggthemes)
library(pillar)
library(baseballr)
library(readr)
library(viridis)
```

### Read Statcast Dataset

```{r}

# Statcast_Combined_Pitches <- read.csv("StatcastCombinedPitches.csv")

Joined_FanGraphs_Statcast <- read.csv("Joined_FanGraphs_Statcast.csv")

PitchUse <- read.csv("PitchUse.csv")

```

### The Proportion Each Pitch Type Was Thrown Each Year

```{r}
# Use of Each Fastpitch Per Year
fastball_frequency_graph <- PitchUse |> 
  filter(pitch_name %in% c("4-Seam Fastball", "Cutter", "Sinker")) |> 
ggplot(aes(x = year, y = prop, fill = year)) +
  geom_bar(stat = "identity") +
  facet_wrap(~pitch_name) +
  labs(title = "Use of Each Fastball Type Per Year",
       x = "Year",
       y = "Proportion") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 11),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white"))

fastball_frequency_graph

# Use of Each Offspeed Per Year
offspeed_frequency_graph <- PitchUse |> 
  filter(pitch_name %in% c("Changeup", "Forkball", "Knuckle Curve", "Split-Finger")) |> 
ggplot(aes(x = year, y = prop, fill = year)) +
  geom_bar(stat = "identity") +
  facet_wrap(~pitch_name) +
   labs(title = "Use of Each Offspeed Type Per Year",
       x = "Year",
       y = "Proportion") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour= "black"),
strip.text.x = element_text(color = "white"))

offspeed_frequency_graph

# Use of Each Breaking Ball Per Year
BreakingBall_frequency_graph <- PitchUse |> 
  filter(pitch_name %in% c("Curveball", "Knuckleball", "Slider")) |> 
ggplot(aes(x = year, y = prop, fill = year)) +
  geom_bar(stat = "identity") +
  facet_wrap(~pitch_name) +
   labs(title = "Use of Each Breaking Ball Type Per Year",
       x = "Year",
       y = "Proportion") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
         axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white"))

BreakingBall_frequency_graph
```

### Filtering Pitchers For IP & Times The Pitcher Throws The Pitch

```{r}
Joined_FanGraphs_Statcast_FF <- Joined_FanGraphs_Statcast |> 
  filter(IP >= 21.1, times_thrown_FF >= 100) 
```


### Relationship Between A Pitcher's Average Velocity and Outcome Variables For A Fastball

```{r}
# Relationship Between A Pitcher's Average 4-Seam Fastball Velocity And Its Average Stuff+

Joined_FanGraphs_Statcast_FF |> 
  ggplot(aes(x = avg_velocity_FF, y = stuff_plus_stuff_FF)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Velocity And Its Average Stuff+",
       x = "Pitcher's Average Velocity",
       y = "Pitcher's Average Stuff+") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  coord_cartesian(ylim = c(0, 200)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 11.2),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```   

```{r}
# Relationship Between A Pitcher's Average 4-Seam Fastball Velocity And Its Run Value Per 100 Pitches

Joined_FanGraphs_Statcast_FF |> 
  ggplot(aes(x = avg_velocity_FF, y = run_value_per100_FF)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Velocity And Its Run Value Per 100 Pitches",
       x = "Pitcher's Average Velocity",
       y = "Pitcher's Run Value Per 100 Pitches") +
  coord_cartesian(ylim = c(-10, 7.5)) +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average 4-Seam Fastball Velocity And Its Swing Rate

Joined_FanGraphs_Statcast_FF |> 
  ggplot(aes(x = avg_velocity_FF, y = swing_rate_FF)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Velocity And Its Swing Rate",
       x = "Pitcher's Average Velocity",
       y = "Pitcher's Swing Rate") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  coord_cartesian(ylim = c(0.2, 0.65)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 11),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average 4-Seam Fastball Velocity And Its Swing And Miss Percentage

Joined_FanGraphs_Statcast_FF |> 
  mutate(swing_and_miss_pct_FF = swing_and_miss_pct_FF / 100) |> 
  ggplot(aes(x = avg_velocity_FF, y = swing_and_miss_pct_FF)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Velocity And Its Swing & Miss Percentage",
       x = "Pitcher's Average Velocity",
       y = "Pitcher's Swing And Miss Percentage") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  coord_cartesian(ylim = c(0, .3)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average 4-Seam Fastball Velocity And WIFF Rate

Joined_FanGraphs_Statcast_FF |> 
  ggplot(aes(x = avg_velocity_FF, y = wiff_rate_FF)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Velocity And Its Wiff Rate",
       x = "Pitcher's Average Velocity",
       y = "Pitcher's Wiff Rate") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
    coord_cartesian(ylim = c(0, 0.5)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 12),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average 4-Seam Fastball Velocity And Average WOBA Value

Joined_FanGraphs_Statcast_FF |> 
  ggplot(aes(x = avg_velocity_FF, y = avg_WOBA_FF)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Velocity And Its Average WOBA Value",
       x = "Pitcher's Average Velocity",
       y = "Pitcher's Average WOBA Value") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  coord_cartesian(ylim = c(0, .65)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10.3),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```


### Relationship Between A Pitcher's Average Vertical Break and Outcome Variables For A Fastball

```{r}
# Relationship Between A Pitcher's Average 4-Seam Fastball Vertical Break And Its Average Stuff+

Joined_FanGraphs_Statcast_FF |> 
  ggplot(aes(x = avg_v_break_FF, y = stuff_plus_stuff_FF)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Vertical Break And Its Average Stuff+",
       x = "Pitcher's Average Vertical Break",
       y = "Pitcher's Average Stuff+") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  coord_cartesian(xlim = c(0.25, 1.8), ylim = c(20, 175)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average 4-Seam Fastball Vertical Break And Its Run Value Per 100 Pitches

Joined_FanGraphs_Statcast_FF |> 
  ggplot(aes(x = avg_v_break_FF, y = run_value_per100_FF)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Vertical Break And Its Run Value Per 100 Pitches",
       x = "Pitcher's Average Veritcal Break",
       y = "Pitcher's Run Value Per 100 Pitches") +
  coord_cartesian(xlim = c(0.25, 1.8), ylim = c(-10, 7.5)) +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 9.2),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average 4-Seam Fastball Vertical Break And Its Swing Rate

Joined_FanGraphs_Statcast_FF |> 
  ggplot(aes(x = avg_v_break_FF, y = swing_rate_FF)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Vertical Break And Its Swing Rate",
       x = "Pitcher's Average Veritcal Break",
       y = "Pitcher's Swing Rate") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  coord_cartesian(xlim = c(.25, 1.8), ylim = c(.2, .65)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 11),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average 4-Seam Fastball Vertical Break And Its Swing And Miss Percentage

Joined_FanGraphs_Statcast_FF |> 
  mutate(swing_and_miss_pct_FF = (swing_and_miss_pct_FF / 100)) |> 
  ggplot(aes(x = avg_v_break_FF, y = swing_and_miss_pct_FF)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Vertical Break And Its Swing & Miss Percentage",
       x = "Pitcher's Average Vertical Break",
       y = "Pitcher's Swing And Miss Percentage") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  coord_cartesian(xlim = c(.25, 1.8), ylim = c(0, .30)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 9),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average 4-Seam Fastball Vertical Break And WIFF Rate

Joined_FanGraphs_Statcast_FF |> 
  ggplot(aes(x = avg_v_break_FF, y = wiff_rate_FF)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Vertical Break And Its Wiff Rate",
       x = "Pitcher's Average Vertical Break",
       y = "Pitcher's Wiff Rate") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
    coord_cartesian(xlim = c(0.25, 1.8), ylim = c(0, .6)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 11.2),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average 4-Seam Fastball Vertical Break And Average WOBA Value

Joined_FanGraphs_Statcast_FF |> 
  ggplot(aes(x = avg_v_break_FF, y = avg_WOBA_FF)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Vertical Break And Its Average WOBA Value",
       x = "Pitcher's Average Vertical Break",
       y = "Pitcher's Average WOBA Value") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  coord_cartesian(xlim = c(0.25, 1.8), ylim = c(0, .7)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```


### Relationship Between A Pitcher's Average Horizontal Break and Outcome Variables For A Fastball

```{r}
# Relationship Between A Pitcher's Average 4-Seam Fastball Horizontal Break And Its Average Stuff+

Joined_FanGraphs_Statcast |> 
  ggplot(aes(x = avg_h_break_FF, y = stuff_plus_stuff_FF)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Horizontal Break And Its Average Stuff+",
       x = "Pitcher's Average Horizontal Break",
       y = "Pitcher's Average Stuff+") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  coord_cartesian(ylim = c(0, 200)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average 4-Seam Fastball  Horizontal Break And Its Run Value Per 100 Pitches

Joined_FanGraphs_Statcast |> 
  ggplot(aes(x = avg_h_break_FF, y = run_value_per100_FF)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Horizontal Break And Its Run Value Per 100 Pitches",
       x = "Pitcher's Average Horizontal Break",
       y = "Pitcher's Run Value Per 100 Pitches") +
  coord_cartesian(ylim = c(-10, 10)) +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 9.2),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average 4-Seam Fastball Horizontal Break And Its Swing Rate

Joined_FanGraphs_Statcast |> 
  ggplot(aes(x = avg_h_break_FF, y = swing_rate_FF)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Horizontal Break And Its Swing Rate",
       x = "Pitcher's Average Horizontal Break",
       y = "Pitcher's Swing Rate") +
  geom_smooth(method = "lm", se = FALSE, color = "red") + 
  coord_cartesian(ylim = c(.12, .75)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 11),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average 4-Seam Fastball Horizontal Break And Its Swing And Miss Percentage

Joined_FanGraphs_Statcast |> 
  mutate(swing_and_miss_pct_FF = (swing_and_miss_pct_FF / 100)) |>
  ggplot(aes(x = avg_h_break_FF, y = swing_and_miss_pct_FF)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Horizontal Break And Its Swing & Miss Percentage",
       x = "Pitcher's Average Horizontal Break",
       y = "Pitcher's Swing And Miss Percentage") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  coord_cartesian(ylim = c(0, .35)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 9.2),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average 4-Seam Fastball Horizontal Break And WIFF Rate

Joined_FanGraphs_Statcast |> 
  ggplot(aes(x = avg_h_break_FF, y = wiff_rate_FF)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Horizontal Break And Its Wiff Rate",
       x = "Pitcher's Average Horizontal Break",
       y = "Pitcher's Wiff Rate") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
    coord_cartesian(ylim = c(0, .55)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 11),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average 4-Seam Fastball Horizontal Break And Average WOBA Value

Joined_FanGraphs_Statcast |> 
  ggplot(aes(x = avg_h_break_FF, y = avg_WOBA_FF)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Horizontal Break And Its Average WOBA Value",
       x = "Pitcher's Average Horizontal Break",
       y = "Pitcher's Average WOBA Value") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  coord_cartesian(ylim = c(0, .85)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 9.7),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

### Filtering Pitchers For IP & Times The Pitcher Throws The Pitch

```{r}
Joined_FanGraphs_Statcast_SL <- Joined_FanGraphs_Statcast |> 
  filter(IP >= 21.1, times_thrown_SL >= 100) 
```


### Relationship Between A Pitcher's Average Velocity and Outcome Variables For A Slider


```{r}
# Relationship Between A Pitcher's Average 4-Seam Fastball Velocity And Its Average Stuff+

Joined_FanGraphs_Statcast_SL |> 
  ggplot(aes(x = avg_velocity_SL, y = stuff_plus_stuff_SL)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average Slider Velocity And Its Average Stuff+",
       x = "Pitcher's Average Velocity",
       y = "Pitcher's Average Stuff+") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  coord_cartesian(ylim = c(50, 175)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 12),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average Slider Velocity And Its Run Value Per 100 Pitches

Joined_FanGraphs_Statcast_SL |> 
  ggplot(aes(x = avg_velocity_SL, y = run_value_per100_SL)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average Slider Velocity And Its Run Value Per 100 Pitches",
       x = "Pitcher's Average Velocity",
       y = "Pitcher's Run Value Per 100 Pitches") +
  coord_cartesian(ylim = c(-20, 15)) +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 11.2),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average Slider Velocity And Its Swing Rate

Joined_FanGraphs_Statcast_SL |> 
  ggplot(aes(x = avg_velocity_SL, y = swing_rate_SL)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average Slider Velocity And Its Swing Rate",
       x = "Pitcher's Average Velocity",
       y = "Pitcher's Swing Rate") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 13),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average Slider Velocity And Its Swing And Miss Percentage

Joined_FanGraphs_Statcast_SL |> 
  mutate(swing_and_miss_pct_SL = (swing_and_miss_pct_SL / 100)) |>
  ggplot(aes(x = avg_velocity_SL, y = swing_and_miss_pct_SL)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average Slider Velocity And Its Swing & Miss Percentage",
       x = "Pitcher's Average Velocity",
       y = "Pitcher's Swing And Miss Percentage") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  coord_cartesian(ylim = c(0, .50)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 11.2),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average Slider Velocity And WIFF Rate

Joined_FanGraphs_Statcast_SL |> 
  ggplot(aes(x = avg_velocity_SL, y = wiff_rate_SL)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average Slider Velocity And Its Wiff Rate",
       x = "Pitcher's Average Velocity",
       y = "Pitcher's Wiff Rate") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
    coord_cartesian(ylim = c(0, .6)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 13.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average Slider Velocity And Average WOBA Value

Joined_FanGraphs_Statcast_SL |> 
  ggplot(aes(x = avg_velocity_SL, y = avg_WOBA_SL)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average Slider Velocity And Its Average WOBA Value",
       x = "Pitcher's Average Velocity",
       y = "Pitcher's Average WOBA Value") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  coord_cartesian(ylim = c(0, .85)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 11.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

### Relationship Between A Pitcher's Average Vertical Break and Outcome Variables For A Slider

```{r}
# Relationship Between A Pitcher's Average Slider Vertical Break And Its Average Stuff+

Joined_FanGraphs_Statcast_SL |> 
  ggplot(aes(x = avg_v_break_SL, y = stuff_plus_stuff_SL)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average Slider Vertical Break And Its Average Stuff+",
       x = "Pitcher's Average Vertical Break",
       y = "Pitcher's Average Stuff+") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  coord_cartesian(xlim = c(-1, 1.3), ylim = c(20, 200)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 12),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average Slider Vertical Break And Its Run Value Per 100 Pitches

Joined_FanGraphs_Statcast_SL |> 
  ggplot(aes(x = avg_v_break_SL, y = run_value_per100_SL)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average Slider Vertical Break And Its Run Value Per 100 Pitches",
       x = "Pitcher's Average Veritcal Break",
       y = "Pitcher's Run Value Per 100 Pitches") +
  coord_cartesian(xlim = c(-1, 1.3), ylim = c(-15, 15)) +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10.7),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average Slider Vertical Break And Its Swing Rate

Joined_FanGraphs_Statcast_SL |> 
  ggplot(aes(x = avg_v_break_SL, y = swing_rate_SL)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average Slider Vertical Break And Its Swing Rate",
       x = "Pitcher's Average Veritcal Break",
       y = "Pitcher's Swing Rate") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  coord_cartesian(xlim = c(-1, 1.3)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 12),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average Slider Vertical Break And Its Swing And Miss Percentage

Joined_FanGraphs_Statcast_SL |> 
  mutate(swing_and_miss_pct_SL = (swing_and_miss_pct_SL / 100)) |>
  ggplot(aes(x = avg_v_break_SL, y = swing_and_miss_pct_SL)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average Slider Vertical Break And Its Swing & Miss Percentage",
       x = "Pitcher's Average Vertical Break",
       y = "Pitcher's Swing And Miss Percentage") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  coord_cartesian(xlim = c(-1, 1.3), ylim = c(0, .35)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average Slider Vertical Break And WIFF Rate

Joined_FanGraphs_Statcast_SL |> 
  ggplot(aes(x = avg_v_break_SL, y = wiff_rate_SL)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average Slider Vertical Break And Its Wiff Rate",
       x = "Pitcher's Average Vertical Break",
       y = "Pitcher's Wiff Rate") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
    coord_cartesian(xlim = c(-1, 1.3), ylim = c(0, 1)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 12.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average Slider Vertical Break And Average WOBA Value

Joined_FanGraphs_Statcast_SL |> 
  ggplot(aes(x = avg_v_break_SL, y = avg_WOBA_SL)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average Slider Vertical Break And Its Average WOBA Value",
       x = "Pitcher's Average Vertical Break",
       y = "Pitcher's Average WOBA Value") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  coord_cartesian(xlim = c(-1, 1.3), ylim = c(0, 1)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 11),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```


### Relationship Between A Pitcher's Average Horizontal Break and Outcome Variables For A Slider

```{r}
# Relationship Between A Pitcher's Average Slider Horizontal Break And Its Average Stuff+

Joined_FanGraphs_Statcast_SL |> 
  ggplot(aes(x = avg_h_break_SL, y = stuff_plus_stuff_SL)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average Slider Horizontal Break And Its Average Stuff+",
       x = "Pitcher's Average Horizontal Break",
       y = "Pitcher's Average Stuff+") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  coord_cartesian(xlim = c(-2, 1.75), ylim = c(20, 190)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 11.2),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average Slider Horizontal Break And Its Run Value Per 100 Pitches

Joined_FanGraphs_Statcast_SL |> 
  ggplot(aes(x = avg_h_break_SL, y = run_value_per100_SL)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average Slider Horizontal Break And Its Run Value Per 100 Pitches",
       x = "Pitcher's Average Horizontal Break",
       y = "Pitcher's Run Value Per 100 Pitches") +
  coord_cartesian(xlim = c(-2, 1.75), ylim = c(-15, 15)) +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10.1),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average Slider Horizontal Break And Its Swing Rate

Joined_FanGraphs_Statcast_SL |> 
  ggplot(aes(x = avg_h_break_SL, y = swing_rate_SL)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average Slider Horizontal Break And Its Swing Rate",
       x = "Pitcher's Average Horizontal Break",
       y = "Pitcher's Swing Rate") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  coord_cartesian(xlim = c(-2, 1.75)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 11),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average Slider Horizontal Break And Its Swing And Miss Percentage

Joined_FanGraphs_Statcast_SL |> 
  mutate(swing_and_miss_pct_SL = (swing_and_miss_pct_SL / 100)) |>
  ggplot(aes(x = avg_h_break_SL, y = swing_and_miss_pct_SL)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average Slider Horizontal Break And Its Swing & Miss Percentage",
       x = "Pitcher's Average Horizontal Break",
       y = "Pitcher's Swing And Miss Percentage") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  coord_cartesian(xlim = c(-2, 1.75), ylim = c(0, .45)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 10),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average Slider Horizontal Break And WIFF Rate

Joined_FanGraphs_Statcast_SL |> 
  ggplot(aes(x = avg_h_break_SL, y = wiff_rate_SL)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average Slider Horizontal Break And Its Wiff Rate",
       x = "Pitcher's Average Horizontal Break",
       y = "Pitcher's Wiff Rate") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
    coord_cartesian(xlim = c(-2, 1.75), ylim = c(0, 1)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 12),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Relationship Between A Pitcher's Average Slider Horizontal Break And Average WOBA Value

Joined_FanGraphs_Statcast_SL |> 
  ggplot(aes(x = avg_h_break_SL, y = avg_WOBA_SL)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Relationship Between A Pitcher's Average Slider Horizontal Break And Its Average WOBA Value",
       x = "Pitcher's Average Horizontal Break",
       y = "Pitcher's Average WOBA Value") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  coord_cartesian(xlim = c(-2, 1.75), ylim = c(0, 1)) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 11),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```