---
title: "Important_EDA"
author: "Belle Schmidt"
date: "2024-07-18"
output: html_document
---

### Libraries
```{r}
library(tidyverse)
library(dslabs)
library(broom)
```

### Read Dataset
```{r}
# Reads in data that includes the proportion of times each pitch type was thrown each season and converts season to categorical
pitch_use <- read.csv("PitchUse.csv") |> 
  mutate(year = factor(year, levels = c(2020, 2021, 2022, 2023, 2024)))

# Reads in combined Baseball Savant and Statcast data
pitching_stats <- read.csv("mlb_pitching_stats_2020-24.csv")

# Filters data to only include fastballs and converts season to categorical
fastball_data <- pitching_stats |> 
  filter(pitch_name == "4-Seam Fastball", !is.na(stuff_plus)) |> 
  mutate(season = factor(season, levels = c(2020, 2021, 2022, 2023, 2024)))

# Reads in the dataset that includes the proportion of times a sweeper was used each season
sweeper_use <- read.csv("Sweeper_Use.csv")
```

### Setting The Theme
```{r}
#color_scale <- scale_fill_manual(values = c("#009E73","#F0E442", "#0072B2", "#D55E00", "#CC79A7"))

# Customizes a color scale for the barplots
color_scale <- scale_fill_manual(values = c("darkred","orange2", "darkslategray","darkgoldenrod3", "violetred4")) 

# Customizes a color scale for the scatterplots
color_scale2 <- scale_colour_manual(values = c("darkred","orange2", "darkslategray","darkgoldenrod3", "violetred4"))

# Creates a custom theme for all the plots
theme <- theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12, lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white"))
```

### The Proportion Each Pitch Type Was Thrown Each Year
```{r}
# Graph showing the use of each fastball pitch type per year
fastball_frequency_graph <- pitch_use |> 
  filter(pitch_name %in% c("4-Seam Fastball", "Cutter", "Sinker")) |> 
ggplot(aes(x = year, y = prop, fill = year)) +
  geom_bar(stat = "identity") +
  facet_wrap(~pitch_name) +
  labs(title = "Use of Each Fastball Type Per Year",
       x = "Year",
       y = "Proportion") +
  color_scale +
  theme

fastball_frequency_graph

# Graph showing the use of each off speed pitch type per year
offspeed_frequency_graph <- pitch_use |> 
  filter(pitch_name %in% c("Changeup", "Knuckle Curve", "Split-Finger")) |> 
ggplot(aes(x = year, y = prop, fill = year)) +
  geom_bar(stat = "identity") +
  facet_wrap(~pitch_name) +
   labs(title = "Use of Each Offspeed Type Per Year",
       x = "Year",
       y = "Proportion") +
  color_scale +
  theme

offspeed_frequency_graph

# Graph showing the use of each breaking ball pitch type per year
BreakingBall_frequency_graph <- pitch_use |> 
  filter(pitch_name %in% c("Curveball", "Slider")) |> 
ggplot(aes(x = year, y = prop, fill = year)) +
  geom_bar(stat = "identity") +
  facet_wrap(~pitch_name) +
   labs(title = "Use of Each Breaking Ball Type Per Year",
       x = "Year",
       y = "Proportion") +
  color_scale +
  theme

BreakingBall_frequency_graph
```

### Proportion of Times The Sweeper Was Thrown Each Year
```{r}
# Use of Each Fastpitch Per Year
sweeper_frequency_graph <- sweeper_use|> 
  mutate(year = factor(year, levels = c(2020, 2021, 2022, 2023, 2024))) |> 
  ggplot(aes(x = year, y = prop, fill = year)) +
  facet_wrap(~pitch_name) +
  geom_bar(stat = "identity") +
  labs(title = "Change in Sweeper Usage Each Year",
       x = "Year",
       y = "Proportion") +
  color_scale +
  theme

sweeper_frequency_graph
```

### Relationship Between A Pitcher's Average Velocity and Outcome Variables For A 4-Seam Fastball
```{r}
# Graph of the relationship between a pitcher's average 4-Seam Fastball velocity and its average stuff+

fastball_data |> 
  ggplot(aes(x = velocity, y = stuff_plus)) +
  geom_point(aes(color = season), alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Velocity And Its Average Stuff+",
       x = "Pitcher's Average Velocity",
       y = "Pitcher's Average Stuff+") +
   color_scale2 +
   theme +
   theme(plot.title = element_text(size = 11.2))
```   

```{r}
# Graph of the relationship between a pitcher's average 4-Seam Fastball velocity and whiff percentage

fastball_data |> 
  ggplot(aes(x = velocity, y = whiff_pct)) +
  geom_point(aes(color = season), alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Velocity And Its Whiff Percentage",
       x = "Pitcher's Average Velocity",
       y = "Pitcher's Whiff Percentage") +
  color_scale2 +
  theme +
  theme(plot.title = element_text(size = 11)) 
```

```{r}
# Graph of the relationship between a pitcher's average 4-Seam Fastball velocity and average xwOBA value
fastball_data |> 
  ggplot(aes(x = velocity, y = xwOBA)) +
  geom_point(aes(color = season), alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Velocity And Its Average xwOBA Value",
       x = "Pitcher's Average Velocity",
       y = "Pitcher's Average xwOBA Value") +
  color_scale2 +
  theme +
  theme(plot.title = element_text(size = 10.3)) 
```

### Linear Models For Velocity and Stuff+ or An Outcome Variable

# Function That Calculates The Slope of The Linear Model For Each Year 
```{r}
velocity_slope <- function(tidy_dataset){

  # Calculates the slope of the line for each year
  slope <- tidy_dataset |> 
    select(term, estimate) |> 
  mutate(term = recode(term, "velocity" = "velocity_2020")) |> 
  pivot_wider(names_from = term, values_from = estimate) |> 
  select(velocity_2020:`season2024:velocity`) |> 
  mutate(slope2021 = velocity_2020 + `season2021:velocity`, 
         slope2022 = velocity_2020 + `season2022:velocity`,
         slope2023 = velocity_2020 + `season2023:velocity`,
         slope2024 = velocity_2020 + `season2024:velocity`) |> 
  select(velocity_2020, slope2021:slope2024) |> 
  pivot_longer(cols = c(velocity_2020, slope2021:slope2024), names_to = "season", values_to = "slope") |> 
  mutate(season = str_extract(season, "\\d{4}"))
  
  # Extracts the std_error for each year
  std_error <- tidy_dataset |> 
  mutate(term = recode(term, "velocity" = "velocity_2020")) |>
  select(term, std.error) |> 
  filter(term == c("velocity_2020", "season2021:velocity", "season2022:velocity", "season2023:velocity", "season2024:velocity"))|> 
    rename(season = term) |> 
    mutate(season = str_extract(season, "\\d{4}"))
  
  # Joins the slope and std_erros into one dataset
  full_join(slope, std_error)  
}
```

# Linear Model For Stuff Plus and Velocity
```{r}
# Linear model for velocity and stuff+
velocity_lm <- lm(stuff_plus ~ season * velocity, 
                data = fastball_data) 

summary(velocity_lm)
tidy_velocity_lm <-tidy(velocity_lm)

# Calls the function above that calculates the slope of the linear model for each year
velocity_stuff_plus_slope <- velocity_slope(tidy_velocity_lm)
```

# Graph of Slope For Each Year's Velocity and Stuff+ Linear Model
```{r}
velocity_stuff_plus_slope |> 
  mutate(ymin = slope - std.error, ymax = slope + std.error) |> 
  ggplot() +
  geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") +
  geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) +
  geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) +
  labs(title = "Impact Each MPH of Velocity Has on Stuff+ Per Season",
       x = "Year",
       y = "Change in Stuff+ Per MPH of Velocity") +
  theme + 
  theme(plot.title = element_text(size = 18))
```

# Linear Model For Whiff Percentage and Velocity
```{r}
# Linear model for velocity predicting whiff percentage
velocity_whiff_lm <- lm(whiff_pct ~ season * velocity, 
                data = fastball_data) 

summary(velocity_whiff_lm)
tidy_velocity_whiff_lm <-tidy(velocity_whiff_lm)

# Calls the function above that calculates the slope of the linear model for each year
velocity_whiff_slope <- velocity_slope(tidy_velocity_whiff_lm)
```

# Graph of Slope For Each Year's Velocity and Whiff Percentage Linear Model
```{r}
velocity_whiff_slope |> 
  mutate(ymin = slope - std.error, ymax = slope + std.error) |>
  ggplot() +
  geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") +
  geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) +
  geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) +
  labs(title = "Impact Each MPH of Velocity Has on Whiff Percentage Per Season",
       x = "Year",
       y = "Change in Whiff Percentage Per Additional MPH of Velocity") +
  theme +
  theme(plot.title = element_text(size = 14),
        axis.title.y = element_text(size = 8),
        axis.text.x = element_text(size = 10))
```

# Linear Model For xwOBA and Velocity
```{r}
velocity_xwOBA <- lm(xwOBA ~ season * velocity, 
                data = fastball_data) 


summary(velocity_xwOBA)
tidy_velocity_xwOBA <- tidy(velocity_xwOBA)

# Calls the function above that calculates the slope of the linear model for each year
velocity_xwOBA_slope <- velocity_slope(tidy_velocity_xwOBA)
```

# Graph of Slope For Each Year's Velocity and xwOBA Linear Model
```{r}
velocity_xwOBA_slope |> 
  mutate(ymin = slope - std.error, ymax = slope + std.error) |>
  ggplot() +
  geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") +
  geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) +
  geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) +
  labs(title = "Impact Each MPH of Velocity Has on xwOBA Per Season",
       x = "Year",
       y = "Change in xwOBA Per Additional MPH of Velocity") +
  theme +
  theme(plot.title = element_text(size = 15),
        axis.title.y = element_text(size = 10),
        axis.text.x = element_text(size = 10))
```

### Relationship Between A Pitcher's Average Induced Vertical Break and Stuff+ or Outcome Variables For A 4-Seam Fastball

```{r}
# Graph of the relationship between a pitcher's average 4-Seam Fastball induced vertical break and its average stuff+

fastball_data |> 
  ggplot(aes(x = induced_vertical_break, y = stuff_plus)) +
  geom_point(aes(color = season), alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Vertical Break And Its Average Stuff+",
       x = "Pitcher's Average Induced Vertical Break",
       y = "Pitcher's Average Stuff+") +
  color_scale2 +
  theme +
  theme(plot.title = element_text(size = 11)) 
```

```{r}
# Graph of the relationship between a pitcher's average 4-Seam Fastball induced vertical break and whiff percentage

fastball_data |> 
  ggplot(aes(x = induced_vertical_break, y = whiff_pct)) +
  geom_point(aes(color = season), alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Vertical Break And Its Whiff Percentage",
       x = "Pitcher's Average Induced Vertical Break",
       y = "Pitcher's Whiff Percentage") +
  color_scale2 +
  theme +
  theme(plot.title = element_text(size = 10.5))
```

```{r}
# Graph of the relationship between a pitcher's average 4-Seam Fastball induced vertical break and average xwOBA value

fastball_data |> 
  ggplot(aes(x = induced_vertical_break, y = xwOBA)) +
  geom_point(aes(color = season), alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Vertical Break And Its Average xwOBA Value",
       x = "Pitcher's Average Induced Vertical Break",
       y = "Pitcher's Average xwOBA Value") +
  color_scale2 +
  theme +
  theme(plot.title = element_text(size = 10)) 
```

### Linear Models For Vertical Break and Stuff+ or An Outcome Variable

# Function That Calculates The Slope of The Linear Model For Each Year 
```{r}
induced_vertical_break_slope <- function(tidy_dataset){

  # Calculates the slope of the line for each year
  slope <- tidy_dataset |> 
    select(term, estimate) |> 
  mutate(term = recode(term, "induced_vertical_break" = "induced_vertical_break_2020")) |> 
  pivot_wider(names_from = term, values_from = estimate) |> 
  select(induced_vertical_break_2020:`season2024:induced_vertical_break`) |> 
  mutate(slope2021 = induced_vertical_break_2020 + `season2021:induced_vertical_break`, 
         slope2022 = induced_vertical_break_2020 + `season2022:induced_vertical_break`,
         slope2023 = induced_vertical_break_2020 + `season2023:induced_vertical_break`,
         slope2024 = induced_vertical_break_2020 + `season2024:induced_vertical_break`) |> 
  select(induced_vertical_break_2020, slope2021:slope2024) |> 
  pivot_longer(cols = c(induced_vertical_break_2020, slope2021:slope2024), names_to = "season", values_to = "slope") |> 
  mutate(season = str_extract(season, "\\d{4}"))
  
  # Extracts the std_error for each year
  std_error <- tidy_dataset |> 
  mutate(term = recode(term, "induced_vertical_break" = "induced_vertical_break_2020")) |>
  select(term, std.error) |> 
  filter(term == c("induced_vertical_break_2020", "season2021:induced_vertical_break", "season2022:induced_vertical_break", "season2023:induced_vertical_break", "season2024:induced_vertical_break"))|> 
    rename(season = term) |> 
    mutate(season = str_extract(season, "\\d{4}"))
  
  # Joins the slope and std_errors into one dataset
  full_join(slope, std_error) |> 
}
```

# Linear Model For Stuff Plus and Induced Vertical Break
```{r}
# Linear model for induced_vertical break and stuff+
induced_vertical_break_lm <- lm(stuff_plus ~ season * induced_vertical_break, 
                data = fastball_data) 

summary(induced_vertical_break_lm)
tidy_induced_vertical_break_lm <-tidy(induced_vertical_break_lm)

# Calls the function above that calculates the slope of the linear model for each year
v_break_stuff_plus_slope <- induced_vertical_break_slope(tidy_induced_vertical_break_lm)

v_break_stuff_plus_slope
```

# Graph of Slope For Each Year's Induced Vertical Break and Stuff+ Linear Model
```{r}
v_break_stuff_plus_slope |> 
  mutate(ymin = slope - std.error, ymax = slope + std.error) |>
  ggplot() +
  geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") +
  geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) +
  geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) +
  labs(title = "Impact Each Inch of Induced Vertical Break Has on Stuff+ Per Season",
       x = "Year",
       y = "Change in Stuff+ Per Inch of Induced Vertical Break") +
  theme + 
  theme(plot.title = element_text(size = 15),
        axis.title.y = element_text(size = 10),
        axis.text.x = element_text(size = 10))
```

# Linear Model For Whiff Percentage and Induced Vertical Break
```{r}
# Linear model for Induced Vertical break predicting whiff percentage
induced_vertical_break_whiff_lm <- lm(whiff_pct ~ season * induced_vertical_break, 
                data = fastball_data) 

summary(induced_vertical_break_whiff_lm)
tidy_induced_vertical_break_whiff_lm <-tidy(induced_vertical_break_whiff_lm)

# Calls the function above that calculates the slope of the linear model for each year
v_break_whiff_slope <- induced_vertical_break_slope(tidy_induced_vertical_break_whiff_lm)

v_break_whiff_slope
```

# Graph of Slope For Each Year's Induced Vertical Break and Whiff Percentage Linear Model
```{r}
v_break_whiff_slope |> 
  mutate(ymin = slope - std.error, ymax = slope + std.error) |>
  ggplot() +
  geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") +
  geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) +
  geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) +
  labs(title = "Impact Each Inch of Induced Vertical Break Has on Whiff Percentage Per Season",
       x = "Year",
       y = "Change in Whiff Percentage Per Inch of Induced Vertical Break") +
  theme +
  theme(plot.title = element_text(size = 13),
        axis.title.y = element_text(size = 9),
        axis.text.x = element_text(size = 10))
```

# Linear Model For xwOBA and Induced Vertical Break
```{r}
induced_vertical_break_xwOBA <- lm(xwOBA ~ season * induced_vertical_break, 
                data = fastball_data) 


summary(induced_vertical_break_xwOBA)
tidy_induced_vertical_break_xwOBA <- tidy(induced_vertical_break_xwOBA)

# Calls the function above that calculates the slope of the linear model for each year
v_break_xwOBA_slope <- induced_vertical_break_slope(tidy_induced_vertical_break_xwOBA)

```

# Graph of Slope For Each Year's Induced Vertical Break and xwOBA Linear Model
```{r}
v_break_xwOBA_slope |> 
  mutate(ymin = slope - std.error, ymax = slope + std.error) |> 
  ggplot() +
  geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") +
  geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) +
  geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) +
  geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) +
  labs(title = "Impact Each Inch of Induced Vertical Break Has on xwOBA Per Season",
       x = "Year",
       y = "Change in xwOBA Per Inch of Induced Vertical Break") +
  theme +
  theme(plot.title = element_text(size = 13),
        axis.title.y = element_text(size = 10),
        axis.text.x = element_text(size = 10))
```

### Relationship Between A Pitcher's Average Horizontal Break and Stuff+ or Outcome Variables For A 4-Seam Fastball

```{r}
# Graph of the relationship between a pitcher's average 4-Seam Fastball horizontal break and its average stuff+

fastball_data |> 
  ggplot(aes(x = horizontal_break, y = stuff_plus)) +
  geom_point(aes(color = season), alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Horizontal Break And Its Average Stuff+",
       x = "Pitcher's Average Horizontal Break",
       y = "Pitcher's Average Stuff+") +
  color_scale2 +
  theme +
  theme(plot.title = element_text(size = 10)) 
```

```{r}
# Graph of the relationship between a pitcher's average 4-Seam Fastball horizontal break and whiff percentage 
fastball_data |> 
  ggplot(aes(x = horizontal_break, y = whiff_pct)) +
  geom_point(aes(color = season), alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Horizontal Break And Its Whiff Percentage",
       x = "Pitcher's Average Horizontal Break",
       y = "Pitcher's Whiff Percentage") +
  color_scale2 +
  theme +
  theme(plot.title = element_text(size = 10)) 
```

```{r}
# Graph of the relationship between a pitcher's average 4-Seam Fastball horizontal break and average xwOBA value

fastball_data|> 
  ggplot(aes(x = horizontal_break, y = xwOBA)) +
  geom_point(aes(color = season), alpha = .3) +
    geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Horizontal Break And Its Average xwOBA Value",
       x = "Pitcher's Average Horizontal Break",
       y = "Pitcher's Average xwOBA Value") +
  color_scale2 +
  theme +
  theme(plot.title = element_text(size = 9.7)) 
```

### Linear Models For Horizontal Break and Stuff+ or An Outcome Variable

# Function That Calculates The Slope of The Linear Model For Each Year 
```{r}
horizontal_break_slope <- function(tidy_dataset){

  # Calculates the slope of the line for each year
  slope <- tidy_dataset |> 
    select(term, estimate) |> 
  mutate(term = recode(term, "horizontal_break" = "horizontal_break_2020")) |> 
  pivot_wider(names_from = term, values_from = estimate) |> 
  select(horizontal_break_2020:`season2024:horizontal_break`) |> 
  mutate(slope2021 = horizontal_break_2020 + `season2021:horizontal_break`, 
         slope2022 = horizontal_break_2020 + `season2022:horizontal_break`,
         slope2023 = horizontal_break_2020 + `season2023:horizontal_break`,
         slope2024 = horizontal_break_2020 + `season2024:horizontal_break`) |> 
  select(horizontal_break_2020, slope2021:slope2024) |> 
  pivot_longer(cols = c(horizontal_break_2020, slope2021:slope2024), names_to = "season", values_to = "slope") |> 
  mutate(season = str_extract(season, "\\d{4}"))
  
  # Extracts the std_error for each year
  std_error <- tidy_dataset |> 
  mutate(term = recode(term, "horizontal_break" = "horizontal_break_2020")) |>
  select(term, std.error) |> 
  filter(term == c("horizontal_break_2020", "season2021:horizontal_break", "season2022:horizontal_break", "season2023:horizontal_break", "season2024:horizontal_break"))|> 
    rename(season = term) |> 
    mutate(season = str_extract(season, "\\d{4}"))
  
  # Joins the slope and std_erros into one dataset
  full_join(slope, std_error)  
}
```

# Linear Model For Stuff Plus and Horizontal Break
```{r}
# Linear model for horizontal break and stuff+
horizontal_break_lm <- lm(stuff_plus ~ season * horizontal_break, 
                data = fastball_data) 

summary(horizontal_break_lm)
tidy_horizontal_break_lm <-tidy(horizontal_break_lm)

# Calls the function above that calculates the slope of the linear model for each year
h_break_stuff_plus_slope <- horizontal_break_slope(tidy_horizontal_break_lm)

h_break_stuff_plus_slope
```

# Graph of Slope For Each Year's Horizontal Break and Stuff+ Linear Model
```{r}
h_break_stuff_plus_slope |> 
  mutate(ymin = slope - std.error, ymax = slope + std.error) |>
  ggplot() +
  geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") +
  geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) +
  geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) +
  labs(title = "Impact Each Inch of Horizontal Break Has on Stuff+ Per Season",
       x = "Year",
       y = "Change in Stuff+ Per Inch of Horizontal Break") +
  theme + 
  theme(plot.title = element_text(size = 15),
        axis.title.y = element_text(size = 10),
        axis.text.x = element_text(size = 10))
```

# Linear Model For Whiff Percentage and Horizontal Break
```{r}
# Linear model for horizontal break predicting whiff percentage
horizontal_break_whiff_lm <- lm(whiff_pct ~ season * horizontal_break, 
                data = fastball_data) 

summary(horizontal_break_whiff_lm)
tidy_horizontal_break_whiff_lm <-tidy(horizontal_break_whiff_lm)

# Calls the function above that calculates the slope of the linear model for each year
h_break_whiff_slope <- horizontal_break_slope(tidy_horizontal_break_whiff_lm)

h_break_whiff_slope
```

# Graph of Slope For Each Year's Horizontal Break and Whiff Percentage Linear Model
```{r}
h_break_whiff_slope |> 
  mutate(ymin = slope - std.error, ymax = slope + std.error) |>
  ggplot() +
  geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") +
  geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) +
  geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) +
  labs(title = "Impact Each Inch of Horizontal Break Has on Whiff Percentage Per Season",
       x = "Year",
       y = "Change in Whiff Percentage Per Inch of Horizontal Break") +
  theme +
  theme(plot.title = element_text(size = 13),
        axis.title.y = element_text(size = 9),
        axis.text.x = element_text(size = 10))
```

# Linear Model For xwOBA and Horizontal Break
```{r}
horizontal_break_xwOBA <- lm(xwOBA ~ season * horizontal_break, 
                data = fastball_data) 


summary(horizontal_break_xwOBA)
tidy_horizontal_break_xwOBA <- tidy(horizontal_break_xwOBA)

# Calls the function above that calculates the slope of the linear model for each year
h_break_xwOBA_slope <- horizontal_break_slope(tidy_horizontal_break_xwOBA)

h_break_xwOBA_slope
```

# Graph of Slope For Each Year's Horizontal Break and xwOBA Linear Model
```{r}
h_break_xwOBA_slope |> 
  mutate(ymin = slope - std.error, ymax = slope + std.error) |>
  ggplot() +
  geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") +
  geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) +
  geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) +
  labs(title = "Impact Each Inch of Horizontal Break Has on xwOBA Per Season",
       x = "Year",
       y = "Change in xwOBA Per Inch of Horizontal Break") +
  theme +
  theme(plot.title = element_text(size = 13),
        axis.title.y = element_text(size = 10),
        axis.text.x = element_text(size = 10))
```

### Relationship Between a Pitcher's Average Spin Rate and Stuff+ or Outcome Variables for a 4-Seam Fastball

```{r}
# Graph of the relationship between a pitcher's average 4-Seam Fastball spin rate and its average stuff+

fastball_data |> 
  ggplot(aes(x = spin, y = stuff_plus)) +
  geom_point(aes(color = season), alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Spin Rate And Its Average Stuff+",
       x = "Pitcher's Average Spin Rate",
       y = "Pitcher's Average Stuff+") +
  color_scale2 +
  theme +
  theme(plot.title = element_text(size = 11))
```

```{r}
# Graph of the relationship between a pitcher's average 4-Seam Fastball spin rate and whiff percentage

fastball_data |> 
  ggplot(aes(x = spin, y = whiff_pct)) +
  geom_point(aes(color = season), alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Spin Rate And Its Whiff Percentage",
       x = "Pitcher's Average Spin Rate",
       y = "Pitcher's Whiff Percentage") +
  theme +
  color_scale2 +
  theme(plot.title = element_text(size = 11))
```

```{r}
# Graph of the relationship between a pitcher's average 4-Seam Fastball spin rate and average xwOBA value

fastball_data|> 
  ggplot(aes(x = spin, y = xwOBA)) +
  geom_point(aes(color = season), alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Spin Rate And Its Average xwOBA Value",
       x = "Pitcher's Average Spin Rate",
       y = "Pitcher's Average xwOBA Value") +
  color_scale2 +
  theme +
  theme(plot.title = element_text(size = 10.2)) 
```

### Linear Models For Spin and Stuff+ or An Outcome Variable

# Function That Calculates The Slope of The Linear Model For Each Year 
```{r}
spin_slope <- function(tidy_dataset){

  # Calculates the slope of the line for each year
  slope <- tidy_dataset |> 
    select(term, estimate) |> 
  mutate(term = recode(term, "spin" = "spin_2020")) |> 
  pivot_wider(names_from = term, values_from = estimate) |> 
  select(spin_2020:`season2024:spin`) |> 
  mutate(slope2021 = spin_2020 + `season2021:spin`, 
         slope2022 = spin_2020 + `season2022:spin`,
         slope2023 = spin_2020 + `season2023:spin`,
         slope2024 = spin_2020 + `season2024:spin`) |> 
  select(spin_2020, slope2021:slope2024) |> 
  pivot_longer(cols = c(spin_2020, slope2021:slope2024), names_to = "season", values_to = "slope") |> 
  mutate(season = str_extract(season, "\\d{4}"))
  
  # Extracts the std_error for each year
  std_error <- tidy_dataset |> 
  mutate(term = recode(term, "spin" = "spin_2020")) |>
  select(term, std.error) |> 
  filter(term == c("spin_2020", "season2021:spin", "season2022:spin", "season2023:spin", "season2024:spin"))|> 
    rename(season = term) |> 
    mutate(season = str_extract(season, "\\d{4}"))
  
  # Joins the slope and std_errors into one dataset
  full_join(slope, std_error)  
}
```

# Linear Model For Stuff Plus and Spin
```{r}
# Linear model for induced_vertical break and stuff+
spin_lm <- lm(stuff_plus ~ season * spin, 
                data = fastball_data) 

summary(spin_lm)
tidy_spin_lm <-tidy(spin_lm)

# Calls the function above that calculates the slope of the linear model for each year
spin_stuff_plus_slope <- spin_slope(tidy_spin_lm)

spin_stuff_plus_slope
```

# Graph of Slope For Each Year's Spin and Stuff+ Linear Model
```{r}
spin_stuff_plus_slope |> 
  mutate(ymin = slope - std.error, ymax = slope + std.error) |>
  ggplot() +
  geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") +
  geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) +
  geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) +
  labs(title = "Impact Each RPM of Spin Has on Stuff+ Per Season",
       x = "Year",
       y = "Change in Stuff+ Per RPM of Spin") +
  theme + 
  theme(plot.title = element_text(size = 15),
        axis.title.y = element_text(size = 10),
        axis.text.x = element_text(size = 10))
```

# Linear Model For Whiff Percentage and Spin
```{r}
# Linear model for Spin predicting whiff percentage
spin_whiff_lm <- lm(whiff_pct ~ season * spin, 
                data = fastball_data) 

summary(spin_whiff_lm)
tidy_spin_whiff_lm <-tidy(spin_whiff_lm)

# Calls the function above that calculates the slope of the linear model for each year
spin_whiff_slope <- spin_slope(tidy_spin_whiff_lm)

spin_whiff_slope
```

# Graph of Slope For Each Year's Spin and Whiff Percentage Linear Model
```{r}
spin_whiff_slope |> 
  mutate(ymin = slope - std.error, ymax = slope + std.error) |>
  ggplot() +
  geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") +
  geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) +
  geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) +
  labs(title = "Impact Each RPM of Spin Has on Whiff Percentage Per Season",
       x = "Year",
       y = "Change in Whiff Percentage Per RPM of Spin") +
  theme +
  theme(plot.title = element_text(size = 13),
        axis.title.y = element_text(size = 9),
        axis.text.x = element_text(size = 10))
```

# Linear Model For xwOBA and Spin
```{r}
spin_xwOBA <- lm(xwOBA ~ season * spin, 
                data = fastball_data) 


summary(spin_xwOBA)
tidy_spin_xwOBA <- tidy(spin_xwOBA)

# Calls the function above that calculates the slope of the linear model for each year
spin_xwOBA_slope <- spin_slope(tidy_spin_xwOBA)

spin_xwOBA_slope
```

# Graph of Slope For Each Year's Spin and xwOBA Linear Model
```{r}
spin_xwOBA_slope |> 
  mutate(ymin = slope - std.error, ymax = slope + std.error) |>
  ggplot() +
  geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") +
  geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) +
  geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) +
  labs(title = "Impact Each RPM of Spin Has on xwOBA Per Season",
       x = "Year",
       y = "Change in xwOBA Per RPM of Spin") +
  theme +
  theme(plot.title = element_text(size = 13),
        axis.title.y = element_text(size = 10),
        axis.text.x = element_text(size = 10))
```

### Relationship Between A Pitcher's Average Release Extension and Stuff+ or Outcome Variables for a 4-Seam Fastball

```{r}
# Graph of the relationship between a pitcher's average 4-Seam Fastball release extension and its average stuff+

fastball_data|> 
  ggplot(aes(x = extension, y = stuff_plus)) +
  geom_point(aes(color = season), alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Release Extension And Its Average Stuff+",
       x = "Pitcher's Average Release Extension",
       y = "Pitcher's Average Stuff+") +
  color_scale2 +
  theme +
  theme(plot.title = element_text(size = 10)) 
```

```{r}
# Graph of the relationship between a pitcher's average 4-Seam Fastball release extension and whiff percentage

fastball_data |> 
  ggplot(aes(x = extension, y = whiff_pct)) +
  geom_point(aes(color = season), alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Release Extension And Its Whiff Percentage",
       x = "Pitcher's Average Release Extension",
       y = "Pitcher's Whiff Percentage") +
  color_scale2 +
  theme +
  theme(plot.title = element_text(size = 10)) 
```

```{r}
# Graph of the relationship between a pitcher's average 4-Seam Fastball release extension and average xwOBA value

fastball_data |> 
  ggplot(aes(x = extension, y = xwOBA)) +
  geom_point(aes(color = season), alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Between A Pitcher's Average 4-Seam Fastball Release Extension And Its Average xwOBA Value",
       x = "Pitcher's Average Release Extension",
       y = "Pitcher's Average xwOBA Value") +
  color_scale2 +
  theme +
  theme(plot.title = element_text(size = 9.2)) 
```

### Linear Models For Extension and Stuff+ or An Outcome Variable

# Function That Calculates The Slope of The Linear Model For Each Year 
```{r}
extension_slope <- function(tidy_dataset){

  # Calculates the slope of the line for each year
  slope <- tidy_dataset |> 
    select(term, estimate) |> 
  mutate(term = recode(term, "extension" = "extension_2020")) |> 
  pivot_wider(names_from = term, values_from = estimate) |> 
  select(extension_2020:`season2024:extension`) |> 
  mutate(slope2021 = extension_2020 + `season2021:extension`, 
         slope2022 = extension_2020 + `season2022:extension`,
         slope2023 = extension_2020 + `season2023:extension`,
         slope2024 = extension_2020 + `season2024:extension`) |> 
  select(extension_2020, slope2021:slope2024) |> 
  pivot_longer(cols = c(extension_2020, slope2021:slope2024), names_to = "season", values_to = "slope") |> 
  mutate(season = str_extract(season, "\\d{4}"))
  
  # Extracts the std_error for each year
  std_error <- tidy_dataset |> 
  mutate(term = recode(term, "extension" = "extension_2020")) |>
  select(term, std.error) |> 
  filter(term == c("extension_2020", "season2021:extension", "season2022:extension", "season2023:extension", "season2024:extension"))|> 
    rename(season = term) |> 
    mutate(season = str_extract(season, "\\d{4}"))
  
  # Joins the slope and std_errors into one dataset
  full_join(slope, std_error)
}
```

# Linear Model For Stuff Plus and Extension
```{r}
# Linear model for extension and stuff+
extension_lm <- lm(stuff_plus ~ season * extension, 
                data = fastball_data) 

summary(extension_lm)
tidy_extension_lm <-tidy(extension_lm)

# Calls the function above that calculates the slope of the linear model for each year
extension_stuff_plus_slope <- extension_slope(tidy_extension_lm)

extension_stuff_plus_slope
```

# Graph of Slope For Each Year's Extension and Stuff+ Linear Model
```{r}
extension_stuff_plus_slope |> 
  mutate(ymin = slope - std.error, ymax = slope + std.error) |>
  ggplot() +
  geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") +
  geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) +
  geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) +
  labs(title = "Impact Each Foot Strided Has on Stuff+ Per Season",
       x = "Year",
       y = "Change in Stuff+ Per Additional Foot Strided") +
  theme + 
  theme(plot.title = element_text(size = 15),
        axis.title.y = element_text(size = 10),
        axis.text.x = element_text(size = 10))
```

# Linear Model For Whiff Percentage and Extension
```{r}
# Linear model for extension predicting whiff percentage
extension_whiff_lm <- lm(whiff_pct ~ season * extension, 
                data = fastball_data) 

summary(extension_whiff_lm)
tidy_extension_whiff_lm <-tidy(extension_whiff_lm)

# Calls the function above that calculates the slope of the linear model for each year
extension_whiff_slope <- extension_slope(tidy_extension_whiff_lm)

extension_whiff_slope
```

# Graph of Slope For Each Year's Extension and Whiff Percentage Linear Model
```{r}
extension_whiff_slope |> 
  mutate(ymin = slope - std.error, ymax = slope + std.error) |>
  ggplot() +
  geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") +
  geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) +
  geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) +
  labs(title = "Impact Each Additional Foot Strided Has on Whiff Percentage Per Season",
       x = "Year",
       y = "Change in Whiff Percentage Per Additional Foot Strided") +
  theme +
  theme(plot.title = element_text(size = 13),
        axis.title.y = element_text(size = 9),
        axis.text.x = element_text(size = 10))
```

# Linear Model For xwOBA and Extension
```{r}
extension_xwOBA <- lm(xwOBA ~ season * extension, 
                data = fastball_data) 


summary(extension_xwOBA)
tidy_extension_xwOBA <- tidy(extension_xwOBA)

# Calls the function above that calculates the slope of the linear model for each year
extension_xwOBA_slope <- extension_slope(tidy_extension_xwOBA)

extension_xwOBA_slope
```

# Graph of Slope For Each Year's Extension and xwOBA Linear Model
```{r}
extension_xwOBA_slope |> 
  mutate(ymin = slope - std.error, ymax = slope + std.error) |>
  ggplot() +
  geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") +
  geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) +
  geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) +
  labs(title = "Impact Each Additional Foot Strided Has on xwOBA Per Season",
       x = "Year",
       y = "Change in xwOBA Per Additional Foot Strided") +
  theme +
  theme(plot.title = element_text(size = 13),
        axis.title.y = element_text(size = 10),
        axis.text.x = element_text(size = 10))
```
