---
title: "Linear Models with Belle Dataset"
author: "Belle Schmidt"
date: "2024-07-08"
output: html_document
---

# Libraries 
```{r}
library(tidyverse)
library(dslabs)
library(broom)
```

# Read in the dataset
```{r}
Fastball_Data <- read.csv("Fastball_Data.csv")
```


### Linear Model For Stuff Plus and Horizontal Break - With Centering
```{r}

horizontal_break_lm <- lm(stuff_plus_stuff_FF ~ factor(Season) * scale(avg_h_break_FF, scale = F), 
                data = Fastball_Data) 

summary(horizontal_break_lm)
tidy(horizontal_break_lm)

```

### Relationship Between A Pitcher's Average Horizontal Break and Outcome Variables For A Fastball

### Linear Model For Stuff Plus and Horizontal Break - Without Centering
```{r}

horizontal_break_lm <- lm(stuff_plus_stuff_FF ~ factor(Season) * avg_h_break_FF, data = Fastball_Data) 

summary(horizontal_break_lm)

tidy_horizontal_break <- tidy(horizontal_break_lm)

```

### Change of Impact of Horizontal Break On Stuff+ Over Time
```{r}
tidy_horizontal_break_graph <- tidy_horizontal_break |>
  filter(term %in% c("avg_h_break_FF", "factor(Season)2021:avg_h_break_FF", "factor(Season)2022:avg_h_break_FF", "factor(Season)2023:avg_h_break_FF", "factor(Season)2024:avg_h_break_FF")) |> 
  mutate(term = recode(term, "avg_h_break_FF" = "2020"),
         term = str_extract(term, "\\d{4}")) |> 
  ggplot(aes(x = term, y = estimate)) +
  geom_line(size = 1, group = 1, color = "red") +
  geom_point(color = "black", size = 2) +
  labs(title = "Impact Each Inch of Horizontal Break Has on Stuff+ Each Season",
       x = "Year",
       y = "Change in Stuff+ Per Inch of Horizontal Break") +
  theme_bw() +
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 15),
        axis.title.x = element_text(face = "bold", size = 12),
        axis.title.y = element_text(face = "bold", size = 10),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold", size = 10))

tidy_horizontal_break_graph
```

### Linear Model For Aggregated Run Value and Horizontal Break
```{r}

horizontal_break_rv <- lm(run_value_per100_FF ~ factor(Season) * avg_h_break_FF, 
                data = Fastball_Data) 


summary(horizontal_break_rv)

tidy_horizontal_break_rv <- tidy(horizontal_break_rv)

```

### Change of Impact of Horizontal Break On Run Value Over Time
```{r}

tidy_horizontal_break_rv_graph <- tidy_horizontal_break_rv |> 
  filter(term %in% c("avg_h_break_FF", "factor(Season)2021:avg_h_break_FF", "factor(Season)2022:avg_h_break_FF", "factor(Season)2023:avg_h_break_FF", "factor(Season)2024:avg_h_break_FF")) |> 
  mutate(term = recode(term, "avg_h_break_FF" = "2020"),
         term = str_extract(term, "\\d{4}")) |> 
  ggplot(aes(x = term, y = estimate)) +
  geom_line(size = 1, group = 1, color = "red") +
  geom_point(color = "black", size = 2) +
  labs(title = "Impact Each Inch of Horizontal Break Has on Run Value Each Season",
       x = "Year",
       y = "Change in RV Per 100 Pitches Per Inch of Horizontal Break") +
  theme_bw() +
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 14),
        axis.title.x = element_text(face = "bold", size = 12),
        axis.title.y = element_text(face = "bold", size = 9),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold", size = 10))

tidy_horizontal_break_rv_graph
```

```{r}

tidy_horizontal_break_rv_graph <- tidy_horizontal_break_rv |> 
  filter(term %in% c("(Intercept)", "factor(Season)2021", "factor(Season)2022", "factor(Season)2023", "factor(Season)2024")) |> 
  mutate(term = recode(term, "(Intercept)" = "2020"), 
         term = str_extract(term, "\\d{4}")) |> 
  ggplot(aes(x = term, y = estimate)) +
  geom_line(size = 1, group = 1, color = "red") +
  geom_point(color = "black", size = 2) +
  labs(title = "Impact Each Inch of Horizontal Break Has on Run Value Each Season",
       x = "Year",
       y = "Change in RV Per 100 Pitches Per Inch of Horizontal Break") +
  theme_bw() +
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 14),
        axis.title.x = element_text(face = "bold", size = 12),
        axis.title.y = element_text(face = "bold", size = 9),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold", size = 10))

tidy_horizontal_break_rv_graph
```

### Linear Model For Swing And Miss Percentage and Horizontal Break
```{r}

horizontal_break_swing_miss <- lm(swing_and_miss_rate_FF ~ factor(Season) * avg_h_break_FF, 
                data = Fastball_Data) 


summary(horizontal_break_swing_miss)
tidy_horizontal_break_swing_miss <- tidy(horizontal_break_swing_miss)

```


### Change of Impact of Horizontal Break On Swing and Miss Rate Over Time
```{r}

tidy_horizontal_break_swing_miss_graph <- tidy_horizontal_break_swing_miss |> 
  filter(term %in% c("avg_h_break_FF", "factor(Season)2021:avg_h_break_FF", "factor(Season)2022:avg_h_break_FF", "factor(Season)2023:avg_h_break_FF", "factor(Season)2024:avg_h_break_FF")) |> 
  mutate(term = recode(term, "avg_h_break_FF" = "2020"),
         term = str_extract(term, "\\d{4}")) |> 
  ggplot(aes(x = term, y = estimate)) +
  geom_line(size = 1, group = 1, color = "red") +
  geom_point(color = "black", size = 2) +
  labs(title = "Impact Each Inch of Horizontal Break Has on Swing & Miss Rate Each Season",
       x = "Year",
       y = "Change in Swing & Miss Rate Per Inch of Horizontal Break") +
  theme_bw() +
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 12),
        axis.title.x = element_text(face = "bold", size = 12),
        axis.title.y = element_text(face = "bold", size = 8),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold", size = 10))

tidy_horizontal_break_swing_miss_graph

```

### Linear Model For Swing Rate and Horizontal Break
```{r}

horizontal_break_swing_rate <- lm(swing_rate_FF ~ factor(Season) * avg_h_break_FF, 
                data = Fastball_Data) 


summary(horizontal_break_swing_rate)
tidy_horizontal_break_swing_rate <- tidy(horizontal_break_swing_rate)

```

### Change of Impact of Horizontal Break On Swing Rate Over Time
```{r}

tidy_horizontal_break_swing_rate_graph <- tidy_horizontal_break_swing_rate |> 
   filter(term %in% c("avg_h_break_FF", "factor(Season)2021:avg_h_break_FF", "factor(Season)2022:avg_h_break_FF", "factor(Season)2023:avg_h_break_FF", "factor(Season)2024:avg_h_break_FF")) |> 
  mutate(term = recode(term, "avg_h_break_FF" = "2020"),
         term = str_extract(term, "\\d{4}")) |> 
  ggplot(aes(x = term, y = estimate)) +
  geom_line(size = 1, group = 1, color = "red") +
  geom_point(color = "black", size = 2) +
  labs(title = "Impact Each Inch of Horizontal Break Has on Swing Rate Each Season",
       x = "Year",
       y = "Change in Swing Rate Per Inch of Horizontal Break") +
  theme_bw() +
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 13),
        axis.title.x = element_text(face = "bold", size = 12),
        axis.title.y = element_text(face = "bold", size = 9),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold", size = 10))

tidy_horizontal_break_swing_rate_graph
```

### Linear Model For Wiff Rate and Horizontal Break
```{r}

horizontal_break_wiff_rate <- lm(wiff_rate_FF ~ factor(Season) * avg_h_break_FF, 
                data = Fastball_Data) 


summary(horizontal_break_wiff_rate)
tidy_horizontal_break_wiff_rate <- tidy(horizontal_break_wiff_rate)

```

### Change of Impact of Horizontal Break On Wiff Rate Over Time
```{r}
tidy_horizontal_break_wiff_rate_graph <- tidy_horizontal_break_wiff_rate |> 
  filter(term %in% c("avg_h_break_FF", "factor(Season)2021:avg_h_break_FF", "factor(Season)2022:avg_h_break_FF", "factor(Season)2023:avg_h_break_FF", "factor(Season)2024:avg_h_break_FF")) |>
  mutate(term = recode(term, "avg_h_break_FF" = "2020"),
         term = str_extract(term, "\\d{4}")) |> 
  ggplot(aes(x = term, y = estimate)) +
  geom_line(size = 1, group = 1, color = "red") +
  geom_point(color = "black", size = 2) +
  labs(title = "Impact Each Inch of Horizontal Break Has on Wiff Rate Each Season",
       x = "Year",
       y = "Change in Wiff Rate Per Inch of Horizontal Break") +
  theme_bw() +
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 13),
        axis.title.x = element_text(face = "bold", size = 12),
        axis.title.y = element_text(face = "bold", size = 9),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold", size = 10))

tidy_horizontal_break_wiff_rate_graph
```

### Relationship Between A Pitcher's Average Vertical Break and Outcome Variables For A Fastball

### Linear Model For Stuff Plus and Vertical Break - Without Centering
```{r}

vertical_break_lm <- lm(stuff_plus_stuff_FF ~ factor(Season) * avg_v_break_FF, data = Fastball_Data) 

summary(vertical_break_lm)

tidy_vertical_break <- tidy(vertical_break_lm)

```

### Change of Impact of Vertical Break On Stuff+ Over Time
```{r}
tidy_vertical_break_graph <- tidy_vertical_break |> 
  filter(term %in% c("avg_v_break_FF", "factor(Season)2021:avg_v_break_FF", "factor(Season)2022:avg_v_break_FF", "factor(Season)2023:avg_v_break_FF", "factor(Season)2024:avg_v_break_FF")) |>
  mutate(term = recode(term, "avg_v_break_FF" = "2020"),
         term = str_extract(term, "\\d{4}")) |> 
  ggplot(aes(x = term, y = estimate)) +
  geom_line(size = 1, group = 1, color = "red") +
  geom_point(color = "black", size = 2) +
  labs(title = "Impact Each Inch of Vertical Break Has on Stuff+ Each Season",
       x = "Year",
       y = "Change in Stuff+ Per Inch of Vertical Break") +
  theme_bw() +
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 16),
        axis.title.x = element_text(face = "bold", size = 12),
        axis.title.y = element_text(face = "bold", size = 11),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold", size = 10))

tidy_vertical_break_graph
```

### Linear Model For Aggregated Run Value and Vertical Break
```{r}

vertical_break_rv <- lm(run_value_per100_FF ~ factor(Season) * avg_v_break_FF, 
                data = Fastball_Data) 


summary(vertical_break_rv)

tidy_vertical_break_rv <- tidy(vertical_break_rv)

```

### Change of Impact of Vertical Break On Run Value Over Time
```{r}

tidy_vertical_break_rv_graph <- tidy_vertical_break_rv |> 
  filter(term %in% c("avg_v_break_FF", "factor(Season)2021:avg_v_break_FF", "factor(Season)2022:avg_v_break_FF", "factor(Season)2023:avg_v_break_FF", "factor(Season)2024:avg_v_break_FF")) |>
  mutate(term = recode(term, "avg_v_break_FF" = "2020"),
         term = str_extract(term, "\\d{4}")) |> 
  ggplot(aes(x = term, y = estimate)) +
  geom_line(size = 1, group = 1, color = "red") +
  geom_point(color = "black", size = 2) +
  labs(title = "Impact Each Inch of Vertical Break Has on Run Value Each Season",
       x = "Year",
       y = "Change in Run Value Per Inch of Vertical Break") +
  theme_bw() +
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 15),
        axis.title.x = element_text(face = "bold", size = 12),
        axis.title.y = element_text(face = "bold", size = 10),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold", size = 10))

tidy_vertical_break_rv_graph
```

### Linear Model For Swing And Miss Percentage and Vertical Break
```{r}

vertical_break_swing_miss <- lm(swing_and_miss_rate_FF ~ factor(Season) * avg_v_break_FF, 
                data = Fastball_Data) 


summary(vertical_break_swing_miss)
tidy_vertical_break_swing_miss <- tidy(vertical_break_swing_miss)

```


### Change of Impact of Vertical Break On Swing and Miss Rate Over Time
```{r}

tidy_vertical_break_swing_miss_graph <- tidy_vertical_break_swing_miss |> 
  filter(term %in% c("avg_v_break_FF", "factor(Season)2021:avg_v_break_FF", "factor(Season)2022:avg_v_break_FF", "factor(Season)2023:avg_v_break_FF", "factor(Season)2024:avg_v_break_FF")) |>
  mutate(term = recode(term, "avg_v_break_FF" = "2020"),
         term = str_extract(term, "\\d{4}")) |> 
  ggplot(aes(x = term, y = estimate)) +
  geom_line(size = 1, group = 1, color = "red") +
  geom_point(color = "black", size = 2) +
  labs(title = "Impact Each Inch of Vertical Break Has on Swing & Miss Rate Each Season",
       x = "Year",
       y = "Change in Swing & Miss Rate Per Inch of Vertical Break") +
  theme_bw() +
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 13),
        axis.title.x = element_text(face = "bold", size = 12),
        axis.title.y = element_text(face = "bold", size = 9),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold", size = 10))

tidy_vertical_break_swing_miss_graph
```

### Linear Model For Swing Rate and Vertical Break
```{r}

vertical_break_swing_rate <- lm(swing_rate_FF ~ factor(Season) * avg_v_break_FF, 
                data = Fastball_Data) 


summary(vertical_break_swing_rate)
tidy_vertical_break_swing_rate <- tidy(vertical_break_swing_rate)

```

### Change of Impact of Vertical Break On Swing Rate Over Time
```{r}

tidy_vertical_break_swing_rate_graph <- tidy_vertical_break_swing_rate |> 
  filter(term %in% c("avg_v_break_FF", "factor(Season)2021:avg_v_break_FF", "factor(Season)2022:avg_v_break_FF", "factor(Season)2023:avg_v_break_FF", "factor(Season)2024:avg_v_break_FF")) |>
  mutate(term = recode(term, "avg_v_break_FF" = "2020"),
         term = str_extract(term, "\\d{4}")) |> 
  ggplot(aes(x = term, y = estimate)) +
  geom_line(size = 1, group = 1, color = "red") +
  geom_point(color = "black", size = 2) +
  labs(title = "Impact Each Inch of Vertical Break Has on Swing Rate Each Season",
       x = "Year",
       y = "Change in Swing Rate Per Inch of Vertical Break") +
  theme_bw() +
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 13),
        axis.title.x = element_text(face = "bold", size = 12),
        axis.title.y = element_text(face = "bold", size = 9),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold", size = 10))

tidy_vertical_break_swing_rate_graph
```

### Linear Model For Wiff Rate and Vertical Break
```{r}

vertical_break_wiff_rate <- lm(wiff_rate_FF ~ factor(Season) * avg_v_break_FF, 
                data = Fastball_Data) 


summary(vertical_break_wiff_rate)
tidy_vertical_break_wiff_rate <- tidy(vertical_break_wiff_rate)

```

### Change of Impact of Vertical Break On Wiff Rate Over Time
```{r}

tidy_vertical_break_wiff_rate_graph <- tidy_vertical_break_wiff_rate |> 
 filter(term %in% c("avg_v_break_FF", "factor(Season)2021:avg_v_break_FF", "factor(Season)2022:avg_v_break_FF", "factor(Season)2023:avg_v_break_FF", "factor(Season)2024:avg_v_break_FF")) |>
  mutate(term = recode(term, "avg_v_break_FF" = "2020"),
         term = str_extract(term, "\\d{4}")) |> 
  ggplot(aes(x = term, y = estimate)) +
  geom_line(size = 1, group = 1, color = "red") +
  geom_point(color = "black", size = 2) +
  labs(title = "Impact Each Inch of Vertical Break Has on Wiff Rate Each Season",
       x = "Year",
       y = "Change in Wiff Rate Per Inch of Vertical Break") +
  theme_bw() +
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 15),
        axis.title.x = element_text(face = "bold", size = 12),
        axis.title.y = element_text(face = "bold", size = 9),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold", size = 10))

tidy_vertical_break_wiff_rate_graph
```

### Relationship Between A Pitcher's Average Spin Rate and Outcome Variables For A Fastball

### Linear Model For Stuff Plus and Spin Rate - Without Centering
```{r}

spin_rate_lm <- lm(stuff_plus_stuff_FF ~ factor(Season) * avg_spin_rate_FF, data = Fastball_Data) 

summary(spin_rate_lm)

tidy_spin_rate <- tidy(spin_rate_lm)

```

### Change of Impact of Spin Rate On Stuff+ Over Time
```{r}
tidy_spin_rate$term[tidy_spin_rate$term == "avg_spin_rate_FF"] <- "2020"

tidy_spin_rate_graph <- tidy_spin_rate |> 
  filter(term %in% c("2020", "factor(Season)2021:avg_spin_rate_FF", "factor(Season)2022:avg_spin_rate_FF", "factor(Season)2023:avg_spin_rate_FF", "factor(Season)2024:avg_spin_rate_FF")) |>
  mutate(term = str_extract(term, "\\d{4}")) |> 
  ggplot(aes(x = term, y = estimate)) +
  geom_line(size = 1, group = 1, color = "red") +
  geom_point(color = "black", size = 2) +
  labs(title = "Impact Each Unit of Spin Rate Has on Stuff+ Each Season",
       x = "Year",
       y = "Change in Stuff+ Per Unit of Spin Rate") +
  theme_bw() +
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 16),
        axis.title.x = element_text(face = "bold", size = 12),
        axis.title.y = element_text(face = "bold", size = 11),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold", size = 10))

tidy_spin_rate_graph
```

### Linear Model For Aggregated Run Value and Spin Rate
```{r}

spin_rate_rv <- lm(run_value_per100_FF ~ factor(Season) * avg_spin_rate_FF, 
                data = Fastball_Data) 


summary(spin_rate_rv)

tidy_spin_rate_rv <- tidy(spin_rate_rv)

```

### Change of Impact of Spin Rate On Run Value Over Time
```{r}
tidy_spin_rate_rv_graph <- tidy_spin_rate_rv |> 
  mutate(term = str_extract(term, "\\d{4}")) |> 
  filter(term != "(Intercept)") |> 
  ggplot(aes(x = term, y = estimate)) +
  geom_line(size = 1, group = 1, color = "red") +
  geom_point(color = "black", size = 2) +
  labs(title = "Impact Each Unit of Spin Rate Has on Run Value Each Season",
       x = "Year",
       y = "Change in RV Per Unit of Spin Rate") +
  theme_bw() +
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 15),
        axis.title.x = element_text(face = "bold", size = 12),
        axis.title.y = element_text(face = "bold", size = 11),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold", size = 10))


tidy_spin_rate_rv_graph
```

### Linear Model For Swing And Miss Rate and Spin Rate
```{r}

spin_rate_swing_miss <- lm(swing_and_miss_rate_FF ~ factor(Season) * avg_spin_rate_FF, 
                data = Fastball_Data) 


summary(spin_rate_swing_miss)
tidy_spin_rate_swing_miss <- tidy(spin_rate_swing_miss)

```


### Change of Impact of Spin Rate On Swing and Miss Rate Over Time
```{r}
tidy_spin_rate_swing_miss_graph <- tidy_spin_rate_swing_miss |> 
  mutate(term = str_extract(term, "\\d{4}")) |> 
  filter(term != "(Intercept)") |> 
  ggplot(aes(x = term, y = estimate)) +
  geom_line(size = 1, group = 1, color = "red") +
  geom_point(color = "black", size = 2) +
  labs(title = "Impact Each Unit of Spin Rate Has on Swing & Miss Rate Each Season",
       x = "Year",
       y = "Change in Swing & Miss Rate Per Unit of Spin Rate") +
  theme_bw() +
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 14),
        axis.title.x = element_text(face = "bold", size = 12),
        axis.title.y = element_text(face = "bold", size = 10),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold", size = 10))

tidy_spin_rate_swing_miss_graph
```

### Linear Model For Swing Rate and Spin Rate
```{r}

spin_rate_swing_rate <- lm(swing_rate_FF ~ factor(Season) * avg_spin_rate_FF, 
                data = Fastball_Data) 


summary(spin_rate_swing_rate)
tidy_spin_rate_swing_rate <- tidy(spin_rate_swing_rate)

```

### Change of Impact of Spin Rate On Swing Rate Over Time
```{r}
tidy_spin_rate_swing_rate_graph <- tidy_spin_rate_swing_rate |> 
  mutate(term = str_extract(term, "\\d{4}")) |> 
  filter(term != "(Intercept)") |> 
  ggplot(aes(x = term, y = estimate)) +
  geom_line(size = 1, group = 1, color = "red") +
  geom_point(color = "black", size = 2) +
  labs(title = "Impact Each Unit of Spin Rate Has on Swing Rate Each Season",
       x = "Year",
       y = "Change in Swing Rate Per Unit of Spin Rate") +
  theme_bw() +
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 14),
        axis.title.x = element_text(face = "bold", size = 12),
        axis.title.y = element_text(face = "bold", size = 10),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold", size = 10))

tidy_spin_rate_swing_rate_graph
```

### Linear Model For Wiff Rate and Horizontal Break
```{r}

spin_rate_wiff_rate <- lm(wiff_rate_FF ~ factor(Season) * avg_spin_rate_FF, 
                data = Fastball_Data) 


summary(spin_rate_wiff_rate)
tidy_spin_rate_wiff_rate <- tidy(spin_rate_wiff_rate)

```

### Change of Impact of Horizontal Break On Wiff Rate Over Time
```{r}
tidy_spin_rate_wiff_rate_graph <- tidy_spin_rate_wiff_rate |> 
  mutate(term = str_extract(term, "\\d{4}")) |> 
  filter(term != "(Intercept)") |> 
  ggplot(aes(x = term, y = estimate)) +
  geom_line(size = 1, group = 1, color = "red") +
  geom_point(color = "black", size = 2) +
  labs(title = "Impact Each Unit of Spin Rate Has on Wiff Rate Each Season",
       x = "Year",
       y = "Change in Wiff Rate Per Unit of Spin Rate") +
  theme_bw() +
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 14),
        axis.title.x = element_text(face = "bold", size = 12),
        axis.title.y = element_text(face = "bold", size = 10),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold", size = 10))

tidy_spin_rate_wiff_rate_graph
```