---
title: "Linear Models"
author: "Belle Schmidt"
date: "2024-07-08"
output: html_document
---

# Libraries 
```{r}
library(tidyverse)
library(dslabs)
library(broom)
```

# Read in the dataset
```{r}
pitching_stats <- read.csv("mlb_pitching_stats_2020-24.csv")

fastball_data <- pitching_stats|> 
  filter(pitch_name == "4-Seam Fastball", !is.na(stuff_plus)) |> 
  mutate(season = factor(season, levels = c(2020, 2021, 2022, 2023, 2024)))
```

### Horizontal Break and Stuff+ or An Outcome Variable

# Function That Calculates The Slope of The Linear Model For Each Year 
```{r}
horizontal_break_slope <- function(tidy_dataset){
  tidy_dataset |> select(term, estimate) |> 
  mutate(term = recode(term, "horizontal_break" = "horizontal_break_2020")) |> 
  pivot_wider(names_from = term, values_from = estimate) |> 
  select(horizontal_break_2020:`season2024:horizontal_break`) |> 
  mutate(slope2021 = horizontal_break_2020 + `season2021:horizontal_break`, 
         slope2022 = horizontal_break_2020 + `season2022:horizontal_break`,
         slope2023 = horizontal_break_2020 + `season2023:horizontal_break`,
         slope2024 = horizontal_break_2020 + `season2024:horizontal_break`) |> 
  select(horizontal_break_2020, slope2021:slope2024) |> 
  pivot_longer(cols = c(horizontal_break_2020, slope2021:slope2024), names_to = "season", values_to = "slope") |> 
  mutate(season = str_extract(season, "\\d{4}"))
}
```

# Function That Calculates The Standard Error of The Slope For Each Year 
```{r}
# horizontal_break_std_error <- function(tidy_dataset){
#   tidy_horizontal_break_lm |> 
#   select(term, std.error) |> 
#   pivot_wider(names_from = term, values_from = std.error) |> 
#   select(horizontal_break_2020:`season2024:horizontal_break`) |> 
#   mutate(std_error2021 = horizontal_break_2020 + `season2021:horizontal_break`, 
#          std_error2022 = horizontal_break_2020 + `season2022:horizontal_break`,
#          std_error2023 = horizontal_break_2020 + `season2023:horizontal_break`,
#          std_error2024 = horizontal_break_2020 + `season2024:horizontal_break`) |> 
#   select(horizontal_break_2020, std_error2021:std_error2024) |> 
#   pivot_longer(cols = c(horizontal_break_2020, std_error2021:std_error2024), names_to = "season", values_to = "std_error") |> 
#   mutate(season = str_extract(season, "\\d{4}"))
# }
```


# Linear Model For Stuff Plus and Horizontal Break
```{r}
horizontal_break_lm <- lm(stuff_plus ~ season * horizontal_break, 
                data = fastball_data) 

summary(horizontal_break_lm)
tidy_horizontal_break_lm <-tidy(horizontal_break_lm)

tidy_horizontal_break_lm

#horizontal_break_std_error(tidy_horizontal_break_lm)

h_break_stuff_plus_slope <- horizontal_break_slope(tidy_horizontal_break_lm)

h_break_stuff_plus_slope
```

# Graph of Slope For Each Year's Linear Model
```{r}
h_break_stuff_plus_slope |> 
  ggplot() +
  geom_line(aes(x = season, y = slope), size = 1, group = 1, color = "red") +
  geom_point(aes(x = season, y = slope), color = "black", size = 2) +
  labs(title = "Impact Each Inch of Horizontal Break Has on Stuff+ Per Season",
       x = "Year",
       y = "Change in Stuff+ Per Inch of Horizontal Break") +
  theme_bw() +
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size = 15),
        axis.title.x = element_text(face = "bold", size = 12),
        axis.title.y = element_text(face = "bold", size = 10),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold", size = 10))
```

# Linear Model For Aggregated Run Value and Horizontal Break
```{r}

fastball_data
horizontal_break_rv_lm <- lm(run_value_per100 ~ season * horizontal_break, 
                data = fastball_data) 

summary(horizontal_break_rv_lm)
tidy_horizontal_break_rv_lm <- tidy(horizontal_break_rv_lm)

tidy_horizontal_break_rv_lm

#horizontal_break_std_error(tidy_horizontal_break_lm)

h_break_rv_slope <- horizontal_break_slope(tidy_horizontal_break_rv_lm)

h_break_rv_slope
```

# Linear Model For Swing And Miss Percentage and Horizontal Break
```{r}
horizontal_break_swing_miss <- lm(swing_and_miss_pct ~ season * horizontal_break, 
                data = fastball_data) 


summary(horizontal_break_swing_miss)
tidy_horizontal_break_swing_miss <- tidy(horizontal_break_swing_miss)
```

# Linear Model For Swing Percentage and Horizontal Break
```{r}
horizontal_break_swing_pct <- lm(swing_pct ~ season * horizontal_break, 
                data = fastball_data) 


summary(horizontal_break_swing_pct)
tidy_horizontal_break_swing_pct <- tidy(horizontal_break_swing_pct)
```

# Linear Model For Whiff Percentage and Horizontal Break
```{r}
horizontal_break_whiff_pct <- lm(whiff_pct ~ season * horizontal_break, 
                data = fastball_data) 


summary(horizontal_break_whiff_pct)
tidy_horizontal_break_whiff_pct <- tidy(horizontal_break_whiff_pct)
```

# Linear Model For xwOBA and Horizontal Break
```{r}
horizontal_break_xwOBA <- lm(xwOBA ~ season * horizontal_break, 
                data = fastball_data) 


summary(horizontal_break_xwOBA)
tidy_horizontal_break_xwOBA <- tidy(horizontal_break_xwOBA)
```

### Vertical Break and Stuff+ and Outcome Variables

# Linear Model For Stuff Plus and Vertical Break
```{r}
induced_vertical_break_lm <- lm(stuff_plus ~ season * induced_vertical_break, 
                data = fastball_data) 

summary(induced_vertical_break_lm)
tidy(induced_vertical_break_lm)
```

# Linear Model For Aggregated Run Value and Vertical Break
```{r}
induced_vertical_break_lm <- lm(stuff_plus ~ season * induced_vertical_break, 
                data = fastball_data) 

summary(induced_vertical_break)
tidy(induced_vertical_break)
```

# Linear Model For Swing And Miss Percentage and Vertical Break
```{r}
induced_vertical_break_swing_miss <- lm(swing_and_miss_pct ~ season * induced_vertical_break, 
                data = fastball_data) 


summary(induced_vertical_break_swing_miss)
tidy_induced_vertical_break_swing_miss <- tidy(induced_vertical_break_swing_miss)
```

# Linear Model For Swing Percentage and Vertical Break
```{r}
induced_vertical_break_swing_pct <- lm(swing_pct ~ season * induced_vertical_break, 
                data = fastball_data) 


summary(induced_vertical_break_swing_pct)
tidy_induced_vertical_break_swing_pct <- tidy(induced_vertical_break_swing_pct)
```

# Linear Model For Whiff Percentage and Vertical Break
```{r}
induced_vertical_break_whiff_pct <- lm(whiff_pct ~ season * induced_vertical_break, 
                data = fastball_data) 


summary(induced_vertical_break_whiff_pct)
tidy_induced_vertical_break_whiff_pct <- tidy(induced_vertical_break_whiff_pct)
```

# Linear Model For xwOBA and Vertical Break
```{r}
induced_vertical_break_xwOBA <- lm(xwOBA ~ season * induced_vertical_break, 
                data = fastball_data) 


summary(induced_vertical_break_xwOBA)
tidy_induced_vertical_break_xwOBA <- tidy(induced_vertical_break_xwOBA)
```

### Spin Rate and Stuff+ or Outcome Variables

# Linear Model For Stuff Plus and Spin Rate
```{r}
spin_lm <- lm(stuff_plus ~ season * spin, 
                data = fastball_data) 

summary(spin_lm)
tidy(spin_lm)
```

# Linear Model For Aggregated Run Value and Spin
```{r}
spin_rv_lm <- lm(stuff_plus ~ season * spin, 
                data = fastball_data) 

summary(spin_rv_lm)
tidy(spin_rv_lm)
```

# Linear Model For Swing And Miss Percentage and Spin 
```{r}
spin_swing_miss <- lm(swing_and_miss_pct ~ season * spin, 
                data = fastball_data) 


summary(spin_swing_miss)
tidy_spin_swing_miss <- tidy(spin_swing_miss)
```

# Linear Model For Swing Percentage and Spin
```{r}
spin_swing_pct <- lm(swing_pct ~ season * spin, 
                data = fastball_data) 


summary(spin_swing_pct)
tidy_spin_swing_pct <- tidy(spin_swing_pct)
```

# Linear Model For Whiff Percentage and Spin
```{r}
spin_whiff_pct <- lm(whiff_pct ~ season * spin, 
                data = fastball_data) 


summary(spin_whiff_pct)
tidy_spin_whiff_pct <- tidy(spin_whiff_pct)
```

# Linear Model For xwOBA and Spin
```{r}
spin_xwOBA <- lm(xwOBA ~ season * spin, 
                data = fastball_data) 


summary(spin_xwOBA)
tidy_spin_xwOBA <- tidy(spin_xwOBA)
```


### Velocity and Stuff+ or Outcome Variables

# Linear Model For Stuff Plus and Velocity
```{r}
velocity_lm <- lm(stuff_plus ~ season * velocity, 
                data = fastball_data) 

summary(velocity_lm)
tidy(velocity_lm)
```

# Linear Model For Aggregated Run Value and Velocity
```{r}
velocity_rv_lm <- lm(stuff_plus ~ season * velocity, 
                data = fastball_data) 

summary(velocity_rv_lm)
tidy(velocity_rv_lm)
```

# Linear Model For Swing And Miss Percentage and Velocity
```{r}
velocity_swing_miss <- lm(swing_and_miss_pct ~ season * velocity, 
                data = fastball_data) 


summary(velocity_swing_miss)
tidy_velocity_swing_miss <- tidy(velocity_swing_miss)
```

# Linear Model For Swing Percentage and Velocity
```{r}
velocity_swing_pct <- lm(swing_pct ~ season * velocity, 
                data = fastball_data) 


summary(velocity_swing_pct)
tidy_velocity_swing_pct <- tidy(velocity_swing_pct)
```

# Linear Model For Whiff Percentage and Velocity
```{r}
velocity_whiff_pct <- lm(whiff_pct ~ season * velocity, 
                data = fastball_data) 


summary(velocity_whiff_pct)
tidy_velocity_whiff_pct <- tidy(velocity_whiff_pct)
```

# Linear Model For xwOBA and Velocity
```{r}
velocity_xwOBA <- lm(xwOBA ~ season * velocity, 
                data = fastball_data) 


summary(velocity_xwOBA)
tidy_velocity_xwOBA <- tidy(velocity_xwOBA)
```


### Extension and Stuff+ or Outcome Variables

# Linear Model For Stuff Plus and Extension
```{r}
extension_lm <- lm(stuff_plus ~ season * extension, 
                data = fastball_data) 

summary(extension_lm)
tidy(extension_lm)
```

# Linear Model For Aggregated Run Value and Extension
```{r}
extension_rv_lm <- lm(stuff_plus ~ season * extension, 
                data = fastball_data) 

summary(extension_rv_lm)
tidy(extension_rv_lm)
```

# Linear Model For Swing And Miss Percentage and Extension
```{r}
extension_swing_miss <- lm(swing_and_miss_pct ~ season * extension, 
                data = fastball_data) 


summary(extension_swing_miss)
tidy_extension_swing_miss <- tidy(extension_swing_miss)
```

# Linear Model For Swing Percentage and Extension
```{r}
extension_swing_pct <- lm(swing_pct ~ season * extension, 
                data = fastball_data) 


summary(extension_swing_pct)
tidy_extension_swing_pct <- tidy(extension_swing_pct)
```

# Linear Model For Whiff Percentage and Extension
```{r}
extension_whiff_pct <- lm(whiff_pct ~ season * extension, 
                data = fastball_data) 


summary(extension_whiff_pct)
tidy_extension_whiff_pct <- tidy(extension_whiff_pct)
```

# Linear Model For xwOBA and Extension
```{r}
extension_xwOBA <- lm(xwOBA ~ season * extension, 
                data = fastball_data) 


summary(extension_xwOBA)
tidy_extension_xwOBA <- tidy(extension_xwOBA)
```
