---
title: "Linear Models"
author: "Belle Schmidt"
date: "2024-07-08"
output: html_document
---

# Libraries 
```{r}
library(tidyverse)
library(dslabs)
library(broom)
```

# Read in the dataset
```{r}
Overall_Stats <- read.csv("mlb_pitching_stats_2020-24.csv")

Cleaned_Data <- Overall_Stats |> 
  filter(pitch_name == "4-Seam Fastball", !is.na(stuff_plus)) |> 
  mutate(season = factor(season, levels = c(2020, 2021, 2022, 2023, 2024)))
```

### Horizontal Break and Stuff+ or An Outcome Variable

# Linear Model For Stuff Plus and Horizontal Break
```{r}
horizontal_break_lm <- lm(stuff_plus ~ season * horizontal_break, 
                data = Cleaned_Data) 

summary(horizontal_break_lm)
tidy(horizontal_break_lm)
```

# Linear Model For Aggregated Run Value and Horizontal Break
```{r}
horizontal_break_rv_lm <- lm(stuff_plus ~ season * horizontal_break, 
                data = Cleaned_Data) 

summary(horizontal_break_rv_lm)
tidy(horizontal_break_rv_lm)
```

# Linear Model For Swing And Miss Percentage and Horizontal Break
```{r}
horizontal_break_swing_miss <- lm(swing_and_miss_pct ~ season * horizontal_break, 
                data = Cleaned_Data) 


summary(horizontal_break_swing_miss)
tidy_horizontal_break_swing_miss <- tidy(horizontal_break_swing_miss)
```

# Linear Model For Swing Percentage and Horizontal Break
```{r}
horizontal_break_swing_pct <- lm(swing_pct ~ season * horizontal_break, 
                data = Cleaned_Data) 


summary(horizontal_break_swing_pct)
tidy_horizontal_break_swing_pct <- tidy(horizontal_break_swing_pct)
```

# Linear Model For Whiff Percentage and Horizontal Break
```{r}
horizontal_break_whiff_pct <- lm(whiff_pct ~ season * horizontal_break, 
                data = Cleaned_Data) 


summary(horizontal_break_whiff_pct)
tidy_horizontal_break_whiff_pct <- tidy(horizontal_break_whiff_pct)
```

# Linear Model For xwOBA and Horizontal Break
```{r}
horizontal_break_xwOBA <- lm(xwOBA ~ season * horizontal_break, 
                data = Cleaned_Data) 


summary(horizontal_break_xwOBA)
tidy_horizontal_break_xwOBA <- tidy(horizontal_break_xwOBA)
```

### Vertical Break and Stuff+ and Outcome Variables

# Linear Model For Stuff Plus and Vertical Break
```{r}
induced_vertical_break_lm <- lm(stuff_plus ~ season * induced_vertical_break, 
                data = Cleaned_Data) 

summary(induced_vertical_break_lm)
tidy(induced_vertical_break_lm)
```

# Linear Model For Aggregated Run Value and Vertical Break
```{r}
induced_vertical_break_lm <- lm(stuff_plus ~ season * induced_vertical_break, 
                data = Cleaned_Data) 

summary(induced_vertical_break)
tidy(induced_vertical_break)
```

# Linear Model For Swing And Miss Percentage and Vertical Break
```{r}
induced_vertical_break_swing_miss <- lm(swing_and_miss_pct ~ season * induced_vertical_break, 
                data = Cleaned_Data) 


summary(induced_vertical_break_swing_miss)
tidy_induced_vertical_break_swing_miss <- tidy(induced_vertical_break_swing_miss)
```

# Linear Model For Swing Percentage and Vertical Break
```{r}
induced_vertical_break_swing_pct <- lm(swing_pct ~ season * induced_vertical_break, 
                data = Cleaned_Data) 


summary(induced_vertical_break_swing_pct)
tidy_induced_vertical_break_swing_pct <- tidy(induced_vertical_break_swing_pct)
```

# Linear Model For Whiff Percentage and Vertical Break
```{r}
induced_vertical_break_whiff_pct <- lm(whiff_pct ~ season * induced_vertical_break, 
                data = Cleaned_Data) 


summary(induced_vertical_break_whiff_pct)
tidy_induced_vertical_break_whiff_pct <- tidy(induced_vertical_break_whiff_pct)
```

# Linear Model For xwOBA and Vertical Break
```{r}
induced_vertical_break_xwOBA <- lm(xwOBA ~ season * induced_vertical_break, 
                data = Cleaned_Data) 


summary(induced_vertical_break_xwOBA)
tidy_induced_vertical_break_xwOBA <- tidy(induced_vertical_break_xwOBA)
```

### Spin Rate and Stuff+ or Outcome Variables

# Linear Model For Stuff Plus and Spin Rate
```{r}
spin_lm <- lm(stuff_plus ~ season * spin, 
                data = Cleaned_Data) 

summary(spin_lm)
tidy(spin_lm)
```

# Linear Model For Aggregated Run Value and Spin
```{r}
spin_rv_lm <- lm(stuff_plus ~ season * spin, 
                data = Cleaned_Data) 

summary(spin_rv_lm)
tidy(spin_rv_lm)
```

# Linear Model For Swing And Miss Percentage and Spin 
```{r}
spin_swing_miss <- lm(swing_and_miss_pct ~ season * spin, 
                data = Cleaned_Data) 


summary(spin_swing_miss)
tidy_spin_swing_miss <- tidy(spin_swing_miss)
```

# Linear Model For Swing Percentage and Spin
```{r}
spin_swing_pct <- lm(swing_pct ~ season * spin, 
                data = Cleaned_Data) 


summary(spin_swing_pct)
tidy_spin_swing_pct <- tidy(spin_swing_pct)
```

# Linear Model For Whiff Percentage and Spin
```{r}
spin_whiff_pct <- lm(whiff_pct ~ season * spin, 
                data = Cleaned_Data) 


summary(spin_whiff_pct)
tidy_spin_whiff_pct <- tidy(spin_whiff_pct)
```

# Linear Model For xwOBA and Spin
```{r}
spin_xwOBA <- lm(xwOBA ~ season * spin, 
                data = Cleaned_Data) 


summary(spin_xwOBA)
tidy_spin_xwOBA <- tidy(spin_xwOBA)
```


### Velocity and Stuff+ or Outcome Variables

# Linear Model For Stuff Plus and Velocity
```{r}
velocity_lm <- lm(stuff_plus ~ season * velocity, 
                data = Cleaned_Data) 

summary(velocity_lm)
tidy(velocity_lm)
```

# Linear Model For Aggregated Run Value and Velocity
```{r}
velocity_rv_lm <- lm(stuff_plus ~ season * velocity, 
                data = Cleaned_Data) 

summary(velocity_rv_lm)
tidy(velocity_rv_lm)
```

# Linear Model For Swing And Miss Percentage and Velocity
```{r}
velocity_swing_miss <- lm(swing_and_miss_pct ~ season * velocity, 
                data = Cleaned_Data) 


summary(velocity_swing_miss)
tidy_velocity_swing_miss <- tidy(velocity_swing_miss)
```

# Linear Model For Swing Percentage and Velocity
```{r}
velocity_swing_pct <- lm(swing_pct ~ season * velocity, 
                data = Cleaned_Data) 


summary(velocity_swing_pct)
tidy_velocity_swing_pct <- tidy(velocity_swing_pct)
```

# Linear Model For Whiff Percentage and Velocity
```{r}
velocity_whiff_pct <- lm(whiff_pct ~ season * velocity, 
                data = Cleaned_Data) 


summary(velocity_whiff_pct)
tidy_velocity_whiff_pct <- tidy(velocity_whiff_pct)
```

# Linear Model For xwOBA and Velocity
```{r}
velocity_xwOBA <- lm(xwOBA ~ season * velocity, 
                data = Cleaned_Data) 


summary(velocity_xwOBA)
tidy_velocity_xwOBA <- tidy(velocity_xwOBA)
```


### Extension and Stuff+ or Outcome Variables

# Linear Model For Stuff Plus and Extension
```{r}
extension_lm <- lm(stuff_plus ~ season * extension, 
                data = Cleaned_Data) 

summary(extension_lm)
tidy(extension_lm)
```

# Linear Model For Aggregated Run Value and Extension
```{r}
extension_rv_lm <- lm(stuff_plus ~ season * extension, 
                data = Cleaned_Data) 

summary(extension_rv_lm)
tidy(extension_rv_lm)
```

# Linear Model For Swing And Miss Percentage and Extension
```{r}
extension_swing_miss <- lm(swing_and_miss_pct ~ season * extension, 
                data = Cleaned_Data) 


summary(extension_swing_miss)
tidy_extension_swing_miss <- tidy(extension_swing_miss)
```

# Linear Model For Swing Percentage and Extension
```{r}
extension_swing_pct <- lm(swing_pct ~ season * extension, 
                data = Cleaned_Data) 


summary(extension_swing_pct)
tidy_extension_swing_pct <- tidy(extension_swing_pct)
```

# Linear Model For Whiff Percentage and Extension
```{r}
extension_whiff_pct <- lm(whiff_pct ~ season * extension, 
                data = Cleaned_Data) 


summary(extension_whiff_pct)
tidy_extension_whiff_pct <- tidy(extension_whiff_pct)
```

# Linear Model For xwOBA and Extension
```{r}
extension_xwOBA <- lm(xwOBA ~ season * extension, 
                data = Cleaned_Data) 


summary(extension_xwOBA)
tidy_extension_xwOBA <- tidy(extension_xwOBA)
```
