---
title: "Sinkers Relationship Graphs"
author: "Belle Schmidt"
date: "2024-10-27"
output: html_document
---

```{r}
library(tidyverse)
library(dslabs)
library(broom)
library(plotly)
library(gapminder)
library(gridExtra)
library(baseballr)
library(ggthemes)
library(hexbin)
library(gt)
library(gtExtras)
library(ranger) # faster implementation of randomforest library
library(vip) # variable importance
library(scales)

## set theme
theme_set(theme_bw())

# Customizes a color scale for the scatterplots
color_scale2 <- scale_colour_manual(values = c("darkred","orange2", "darkslategray","darkgoldenrod3", "violetred4"))


# Creates a custom theme for all the plots
theme <- theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5, size = 19),
        axis.title = element_text(face = "bold", size = 14),
        axis.text = element_text(face = "bold", size = 13),
        strip.text = element_text(face = "bold", size = 15),
        strip.background = element_rect(fill = "steelblue4", colour = "black", linewidth = 1.0),
        strip.text.x = element_text(color = "white"))
```

```{r}
# Reads in combined Baseball Savant and Statcast data
pitching_stats <- read.csv("mlb_pitching_stats_2021-24_UPDATED.csv")

# Filters data to only include fastballs and converts season to categorical
sinker_data <- pitching_stats |> 
  filter(pitch_name == "Sinker", !is.na(stuff_plus), season %in% c(2021, 2022, 2023, 2024)) |>   
  mutate(season = factor(season))
```


## Velocity

## xwOBA

```{r}
#| fig-width: 12
#| fig-height: 5
#| fig.align: 'center'
# Graph of the relationship between a pitcher's average 4-Seam Fastball velocity and average xwOBA value
sinker_data |> 
  ggplot(aes(x = velocity, y = xwOBA)) +
  geom_point(aes(color = season), alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Between Velocity And xwOBA For A 4-Seam Fastball",
       x = "Pitcher's Average Velocity",
       y = "Pitcher's Average xwOBA Value") +
  color_scale2 +
  theme
```


## Whiff Percentage 

```{r}
#| fig-width: 12
#| fig-height: 5
#| fig.align: 'center'

# Graph of the relationship between a pitcher's average 4-Seam Fastball velocity and whiff percentage
sinker_data |> 
  ggplot(aes(x = velocity, y = whiff_pct)) +
  geom_point(aes(color = season), alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Between Velocity And Whiff% For A 4-Seam Fastball",
       x = "Pitcher's Average Velocity",
       y = "Pitcher's Whiff Percentage") +
  color_scale2 +
  theme
```

## Velocity

```{r}
#| fig-width: 12
#| fig-height: 5
#| fig.align: 'center'

# Graph of the relationship between a pitcher's average 4-Seam Fastball velocity and its average stuff+
sinker_data |> 
  ggplot(aes(x = velocity, y = stuff_plus)) +
  geom_point(aes(color = season), alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Between Velocity And Stuff+ For 4-Seam Fastballs",
       x = "Pitcher's Average Velocity",
       y = "Pitcher's Average Stuff+") +
   color_scale2 +
   theme
```

:::


## Vertical Break 

::: {.panel-tabset}

## xwOBA

```{r}
#| fig-width: 12
#| fig-height: 5
#| fig.align: 'center'

# Graph of the relationship between a pitcher's average 4-Seam Fastball induced vertical break and average xwOBA value

sinker_data |> 
  ggplot(aes(x = induced_vertical_break, y = xwOBA)) +
  geom_point(aes(color = season), alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Between Vertical Break And xwOBA For A 4-Seam Fastball",
       x = "Pitcher's Average Induced Vertical Break",
       y = "Pitcher's Average xwOBA Value") +
  color_scale2 +
  theme
```


## Whiff Percentage 

```{r}
#| fig-width: 12
#| fig-height: 5
#| fig.align: 'center'

# Graph of the relationship between a pitcher's average 4-Seam Fastball induced vertical break and whiff percentage

sinker_data |> 
  ggplot(aes(x = induced_vertical_break, y = whiff_pct)) +
  geom_point(aes(color = season), alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Vertical Break And Whiff% For A 4-Seam Fastball",
       x = "Pitcher's Average Induced Vertical Break",
       y = "Pitcher's Whiff Percentage") +
  color_scale2 +
  theme
```


```{r}
#| fig-width: 12
#| fig-height: 5
#| fig.align: 'center'

# Graph of the relationship between a pitcher's average 4-Seam Fastball induced vertical break and its average stuff+
sinker_data |> 
  ggplot(aes(x = induced_vertical_break, y = stuff_plus)) +
  geom_point(aes(color = season), alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Between Vertical Break And Stuff+ For 4-Seam Fastballs",
       x = "Pitcher's Average Induced Vertical Break",
       y = "Pitcher's Average Stuff+") +
  color_scale2 +
  theme
```

:::

## Horizontal Break  

::: {.panel-tabset}

## xwOBA

```{r}
#| fig-width: 12
#| fig-height: 5
#| fig.align: 'center'

# Graph of the relationship between a pitcher's average 4-Seam Fastball horizontal break and average xwOBA value

sinker_data|> 
  ggplot(aes(x = horizontal_break, y = xwOBA)) +
  geom_point(aes(color = season), alpha = .3) +
    geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Between Horizontal Break And xwOBA For A 4-Seam Fastball",
       x = "Pitcher's Average Horizontal Break",
       y = "Pitcher's Average xwOBA Value") +
  color_scale2 +
  theme
```

## Whiff Percentage 

```{r}
#| fig-width: 12
#| fig-height: 5
#| fig.align: 'center'

# Graph of the relationship between a pitcher's average 4-Seam Fastball horizontal break and whiff percentage 
sinker_data |> 
  ggplot(aes(x = horizontal_break, y = whiff_pct)) +
  geom_point(aes(color = season), alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Between Horizontal Break And Whiff% For A 4-Seam Fastball",
       x = "Pitcher's Average Horizontal Break",
       y = "Pitcher's Whiff Percentage") +
  color_scale2 +
  theme
```

```{r}
#| fig-width: 12
#| fig-height: 5
#| fig.align: 'center'

# Graph of the relationship between a pitcher's average 4-Seam Fastball horizontal break and its average stuff+

sinker_data |> 
  ggplot(aes(x = horizontal_break, y = stuff_plus)) +
  geom_point(aes(color = season), alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Between Horizontal Break And Stuff+ For 4-Seam Fastballs",
       x = "Pitcher's Average Horizontal Break",
       y = "Pitcher's Average Stuff+") +
  color_scale2 +
  theme
```


:::

## Spin Rate   

::: {.panel-tabset}

## xwOBA

```{r}
#| fig-width: 12
#| fig-height: 5
#| fig.align: 'center'

# Graph of the relationship between a pitcher's average 4-Seam Fastball spin rate and average xwOBA value
sinker_data|> 
  ggplot(aes(x = spin, y = xwOBA)) +
  geom_point(aes(color = season), alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Between Spin And xwOBA For A 4-Seam Fastball",
       x = "Pitcher's Average Spin Rate",
       y = "Pitcher's Average xwOBA") +
  color_scale2 +
  theme 
```


## Whiff Percentage 

```{r}
#| fig-width: 12
#| fig-height: 5
#| fig.align: 'center'

# Graph of the relationship between a pitcher's average 4-Seam Fastball spin rate and whiff percentage
sinker_data |> 
  ggplot(aes(x = spin, y = whiff_pct)) +
  geom_point(aes(color = season), alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Between Spin And Whiff Percentage For A 4-Seam Fastball",
       x = "Pitcher's Average Spin Rate",
       y = "Pitcher's Whiff Percentage") +
  theme +
  color_scale2
```


:::

## Extension   

::: {.panel-tabset}

## xwOBA

```{r}
#| fig-width: 12
#| fig-height: 5
#| fig.align: 'center'

# Graph of the relationship between a pitcher's average 4-Seam Fastball release extension and average xwOBA value
sinker_data |> 
  ggplot(aes(x = extension, y = xwOBA)) +
  geom_point(aes(color = season), alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Extension And xwOBA For A 4-Seam Fastball",
       x = "Pitcher's Average Extension",
       y = "Pitcher's Average xwOBA Value") +
  color_scale2 +
  theme
```


## Whiff Percentage 

```{r}
#| fig-width: 12
#| fig-height: 5
#| fig.align: 'center'

# Graph of the relationship between a pitcher's average 4-Seam Fastball release extension and whiff percentage
sinker_data |> 
  ggplot(aes(x = extension, y = whiff_pct)) +
  geom_point(aes(color = season), alpha = .3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  facet_wrap(~season) +
  labs(title = "Relationship Extension And Whiff Percentage For A 4-Seam Fastball",
       x = "Pitcher's Average Extension",
       y = "Pitcher's Whiff Percentage") +
  color_scale2 +
  theme 
```

:::
:::


```{r}
velocity_slope <- function(tidy_dataset){

  # Calculates the slope of the line for each year
  slope <- tidy_dataset |> 
    select(term, estimate) |> 
  mutate(term = recode(term, "velocity" = "velocity_2021")) |> 
  pivot_wider(names_from = term, values_from = estimate) |> 
  select(velocity_2021:`season2024:velocity`) |> 
  mutate(slope2022 = velocity_2021 + `season2022:velocity`, 
         slope2023 = velocity_2021 + `season2023:velocity`,
         slope2024 = velocity_2021 + `season2024:velocity`) |> 
  select(velocity_2021, slope2022, slope2023, slope2024) |> 
  pivot_longer(cols = c(velocity_2021, slope2022:slope2024), names_to = "season", values_to = "slope") |> 
  mutate(season = str_extract(season, "\\d{4}"))
  
  # Extracts the std_error for each year
  std_error <- tidy_dataset |> 
  mutate(term = recode(term, "velocity" = "velocity_2021")) |>
  select(term, std.error) |> 
  filter(term == c("velocity_2021", "season2022:velocity", "season2023:velocity", "season2024:velocity"))|> 
    rename(season = term) |> 
    mutate(season = str_extract(season, "\\d{4}"))
  
  # Joins the slope and std_erros into one dataset
  full_join(slope, std_error)  
}
```

```{r}
# Linear Model For Stuff Plus and Velocity
# Linear model for velocity and stuff+
velocity_lm <- lm(stuff_plus ~ season * velocity, 
                data = sinker_data) 

summary(velocity_lm)
tidy_velocity_lm <-tidy(velocity_lm)

# Calls the function above that calculates the slope of the linear model for each year
velocity_stuff_plus_slope <- velocity_slope(tidy_velocity_lm)
```

```{r}
# Linear model for velocity predicting whiff percentage
velocity_whiff_lm <- lm(whiff_pct ~ season * velocity, 
                data = sinker_data) 

summary(velocity_whiff_lm)
tidy_velocity_whiff_lm <-tidy(velocity_whiff_lm)

# Calls the function above that calculates the slope of the linear model for each year
velocity_whiff_slope <- velocity_slope(tidy_velocity_whiff_lm)
```

```{r}
# Linear Model For xwOBA and Velocity
velocity_xwOBA <- lm(xwOBA ~ season * velocity, 
                data = sinker_data) 


summary(velocity_xwOBA)
tidy_velocity_xwOBA <- tidy(velocity_xwOBA)

# Calls the function above that calculates the slope of the linear model for each year
velocity_xwOBA_slope <- velocity_slope(tidy_velocity_xwOBA)
```

# ```{r}
# # Linear Model For xwOBAcon and Velocity
# velocity_wOBAcon <- lm(wOBA_on_contact ~ season * velocity, 
#                 data = sinker_data) 
# 
# summary(velocity_wOBAcon)
# tidy_velocity_wOBAcon <- tidy(velocity_wOBAcon)
# 
# # Calls the function above that calculates the slope of the linear model for each year
# velocity_wOBAcon_slope <- velocity_slope(tidy_velocity_wOBAcon)
# ```

## Velocity

::: {.panel-tabset}

## Stuff+ And wxOBA

```{r}
#| fig-width: 12
#| fig-height: 5
#| fig.align: 'center'

# Graph of Slope For Each Year's Velocity and Stuff+ Linear Model
stuff_plus <- velocity_stuff_plus_slope |> 
  mutate(ymin = slope - std.error, ymax = slope + std.error) |> 
  ggplot() +
  geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") +
  geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) +
  geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) +
  labs(title = "Velocity's Impact on Stuff+",
       x = "Year",
       y = "Change in Stuff+ Per MPH of Velocity") +
  theme + 
  theme(axis.title.y = element_text(size = 10),
        axis.text.x = element_text(size = 10))


# Graph of Slope For Each Year's Velocity and xwOBA Linear Model
xwOBA <- velocity_xwOBA_slope |> 
  mutate(ymin = slope - std.error, ymax = slope + std.error) |>
  ggplot() +
  geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") +
  geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) +
  geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) +
  labs(title = "Velocity's Impact on xwOBA",
       x = "Year",
       y = "Change in xwOBA Per MPH of Velocity") +
  theme +
  theme(axis.title.y = element_text(size = 10),
        axis.text.x = element_text(size = 10))

grid.arrange(stuff_plus, xwOBA, ncol=2)

```

<!-- ## Stuff+ And wOBAcon -->

<!-- ```{r} -->
<!-- #| fig-width: 12 -->
<!-- #| fig-height: 5 -->
<!-- #| fig.align: 'center' -->

<!-- # Graph of Slope For Each Year's Velocity and Stuff+ Linear Model -->
<!-- stuff_plus <- velocity_stuff_plus_slope |> -->
<!--   mutate(ymin = slope - std.error, ymax = slope + std.error) |> -->
<!--   ggplot() + -->
<!--   geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") + -->
<!--   geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) + -->
<!--   geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) + -->
<!--   labs(title = "Velocity's Impact on Stuff+", -->
<!--        x = "Year", -->
<!--        y = "Change in Stuff+ Per MPH of Velocity") + -->
<!--   theme + -->
<!--   theme(axis.title.y = element_text(size = 10), -->
<!--         axis.text.x = element_text(size = 10)) -->


<!-- # Graph of Slope For Each Year's Velocity and xwOBA Linear Model -->
<!-- wOBAcon <- velocity_wOBAcon_slope |> -->
<!--   mutate(ymin = slope - std.error, ymax = slope + std.error) |> -->
<!--   ggplot() + -->
<!--   geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") + -->
<!--   geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) + -->
<!--   geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) + -->
<!--   labs(title = "Velocity's Impact on wOBAcon", -->
<!--        x = "Year", -->
<!--        y = "Change in wOBAcon Per MPH of Velocity") + -->
<!--   theme + -->
<!--   theme(axis.title.y = element_text(size = 10), -->
<!--         axis.text.x = element_text(size = 10)) -->

<!-- grid.arrange(stuff_plus, wOBAcon, ncol=2) -->

<!-- ``` -->

## Stuff+ And Whiff Percentage

```{r}
#| fig-width: 12
#| fig-height: 5
#| fig.align: 'center'

# Graph of Slope For Each Year's Velocity and Whiff Percentage Linear Model
velocity_whiff <- velocity_whiff_slope |> 
  mutate(ymin = slope - std.error, ymax = slope + std.error) |>
  ggplot() +
  geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") +
  geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) +
  geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) +
  labs(title = "Velocity's Impact on Whiff%",
       x = "Year",
       y = "Change in Whiff% Per  MPH of Velocity") +
  theme +
  theme(axis.title.y = element_text(size = 10),
        axis.text.x = element_text(size = 10))

grid.arrange(stuff_plus, velocity_whiff, ncol=2)
```

:::

## Vertical Movement
```{r}
### Linear Models For Vertical Break and Stuff+ or An Outcome Variable

# Function That Calculates The Slope of The Linear Model For Each Year 
induced_vertical_break_slope <- function(tidy_dataset){

  # Calculates the slope of the line for each year
  slope <- tidy_dataset |> 
    select(term, estimate) |> 
  mutate(term = recode(term, "induced_vertical_break" = "induced_vertical_break_2021")) |> 
  pivot_wider(names_from = term, values_from = estimate) |> 
  select(induced_vertical_break_2021:`season2024:induced_vertical_break`) |> 
  mutate(slope2022 = induced_vertical_break_2021 + `season2022:induced_vertical_break`, 
         slope2023 = induced_vertical_break_2021 + `season2023:induced_vertical_break`,
         slope2024 = induced_vertical_break_2021 + `season2024:induced_vertical_break`) |> 
  select(induced_vertical_break_2021, slope2022, slope2023, slope2024) |> 
  pivot_longer(cols = c(induced_vertical_break_2021, slope2022, slope2023, slope2024), names_to = "season", values_to = "slope") |> 
  mutate(season = str_extract(season, "\\d{4}"))
  
  # Extracts the std_error for each year
  std_error <- tidy_dataset |> 
  mutate(term = recode(term, "induced_vertical_break" = "induced_vertical_break_2021")) |>
  select(term, std.error) |> 
  filter(term == c("induced_vertical_break_2021", "season2022:induced_vertical_break", "season2023:induced_vertical_break", "season2024:induced_vertical_break"))|> 
    rename(season = term) |> 
    mutate(season = str_extract(season, "\\d{4}"))
  
  # Joins the slope and std_errors into one dataset
  full_join(slope, std_error)
}
```

```{r}
# Linear model for induced_vertical break and stuff+
induced_vertical_break_lm <- lm(stuff_plus ~ season * induced_vertical_break, 
                data = sinker_data) 

tidy_induced_vertical_break_lm <-tidy(induced_vertical_break_lm)

# Calls the function above that calculates the slope of the linear model for each year
v_break_stuff_plus_slope <- induced_vertical_break_slope(tidy_induced_vertical_break_lm)


# Linear model for Induced Vertical break predicting whiff percentage
induced_vertical_break_whiff_lm <- lm(whiff_pct ~ season * induced_vertical_break, 
                data = sinker_data) 

tidy_induced_vertical_break_whiff_lm <-tidy(induced_vertical_break_whiff_lm)

# Calls the function above that calculates the slope of the linear model for each year
v_break_whiff_slope <- induced_vertical_break_slope(tidy_induced_vertical_break_whiff_lm)

# Linear Model For xwOBA and Induced Vertical Break
induced_vertical_break_xwOBA <- lm(xwOBA ~ season * induced_vertical_break, 
                data = sinker_data) 


tidy_induced_vertical_break_xwOBA <- tidy(induced_vertical_break_xwOBA)

# Calls the function above that calculates the slope of the linear model for each year
v_break_xwOBA_slope <- induced_vertical_break_slope(tidy_induced_vertical_break_xwOBA)
```

::: {.panel-tabset}

## Stuff+ And xwOBA

```{r}
#| fig-width: 12
#| fig-height: 5
#| fig.align: 'center'

# Graph of Slope For Each Year's Induced Vertical Break and Stuff+ Linear Model
stuff_plus_vertical <- v_break_stuff_plus_slope |> 
  mutate(ymin = slope - std.error, ymax = slope + std.error) |>
  ggplot() +
  geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") +
  geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) +
  geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) +
  labs(title = "Vertical Break's Impact on Stuff+",
      x = "Year",
      y = "Change in Stuff+ Per Inch of Induced Vertical Break") +
  theme + 
  theme(axis.title.y = element_text(size = 9.5),
        axis.text.x = element_text(size = 10))
 
xwOBA_vertical <- v_break_xwOBA_slope |> 
  mutate(ymin = slope - std.error, ymax = slope + std.error) |> 
  ggplot() +
  geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") +
  geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) +
  geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) +
  geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) +
  labs(title = "Vertical Break's Impact on xwOBA",
       x = "Year",
       y = "Change in xwOBA Per Inch of Induced Vertical Break") +
  theme +
  theme(axis.title.y = element_text(size = 9.5),
        axis.text.x = element_text(size = 10))

grid.arrange(stuff_plus_vertical, xwOBA_vertical, ncol=2)
```


## Stuff+ And Whiff Percentage

```{r}
#| fig-width: 12
#| fig-height: 5
#| fig.align: 'center'

# Graph of Slope For Each Year's Induced Vertical Break and Whiff Percentage Linear Model
whiff_vertical <- v_break_whiff_slope |>
  mutate(ymin = slope - std.error, ymax = slope + std.error) |>
  ggplot() +
  geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") +
  geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) +
  geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) +
  labs(title = "Vertical Break's Impact on Whiff%",
       x = "Year",
       y = "Change in Whiff% Per Inch of Induced Vertical Break") +
  theme +
  theme(axis.title.y = element_text(size = 9.5),
        axis.text.x = element_text(size = 10))

grid.arrange(stuff_plus_vertical, whiff_vertical, ncol=2)
```

:::

## Horizontal Movement

::: {.panel-tabset}

```{r}
# Function That Calculates The Slope of The Linear Model For Each Year 
horizontal_break_slope <- function(tidy_dataset){

  # Calculates the slope of the line for each year
  slope <- tidy_dataset |> 
    select(term, estimate) |> 
  mutate(term = recode(term, "horizontal_break" = "horizontal_break_2021")) |> 
  pivot_wider(names_from = term, values_from = estimate) |> 
  select(horizontal_break_2021:`season2024:horizontal_break`) |> 
  mutate(slope2022 = horizontal_break_2021 + `season2022:horizontal_break`,
         slope2023 = horizontal_break_2021 + `season2023:horizontal_break`,
         slope2024 = horizontal_break_2021 + `season2024:horizontal_break`) |> 
  select(horizontal_break_2021, slope2022:slope2024) |> 
  pivot_longer(cols = c(horizontal_break_2021, slope2022, slope2023, slope2024), names_to = "season", values_to = "slope") |> 
  mutate(season = str_extract(season, "\\d{4}"))
  
  # Extracts the std_error for each year
  std_error <- tidy_dataset |> 
  mutate(term = recode(term, "horizontal_break" = "horizontal_break_2021")) |>
  select(term, std.error) |> 
  filter(term == c("horizontal_break_2021", "season2022:horizontal_break", "season2023:horizontal_break", "season2024:horizontal_break"))|> 
    rename(season = term) |> 
    mutate(season = str_extract(season, "\\d{4}"))
  
  # Joins the slope and std_erros into one dataset
  full_join(slope, std_error)  
}

# Linear model for horizontal break and stuff+
horizontal_break_lm <- lm(stuff_plus ~ season * horizontal_break, 
                data = sinker_data) 

tidy_horizontal_break_lm <-tidy(horizontal_break_lm)

# Calls the function above that calculates the slope of the linear model for each year
h_break_stuff_plus_slope <- horizontal_break_slope(tidy_horizontal_break_lm)

# Linear model for horizontal break predicting whiff percentage
horizontal_break_whiff_lm <- lm(whiff_pct ~ season * horizontal_break, 
                data = sinker_data) 

tidy_horizontal_break_whiff_lm <-tidy(horizontal_break_whiff_lm)

# Calls the function above that calculates the slope of the linear model for each year
h_break_whiff_slope <- horizontal_break_slope(tidy_horizontal_break_whiff_lm)

horizontal_break_xwOBA <- lm(xwOBA ~ season * horizontal_break, 
                data = sinker_data) 


tidy_horizontal_break_xwOBA <- tidy(horizontal_break_xwOBA)

# Calls the function above that calculates the slope of the linear model for each year
h_break_xwOBA_slope <- horizontal_break_slope(tidy_horizontal_break_xwOBA)


# horizontal_break_wOBAcon <- lm(wOBA_on_contact ~ season * horizontal_break, 
#                 data = sinker_data) 
# 
# 
# tidy_horizontal_break_wOBAcon <- tidy(horizontal_break_wOBAcon)
# 
# # Calls the function above that calculates the slope of the linear model for each year
# h_break_wOBAcon_slope <- horizontal_break_slope(tidy_horizontal_break_wOBAcon)
```

## Stuff+ And xwOBA

```{r}
#| fig-width: 12
#| fig-height: 5
#| fig.align: 'center'

# Graph of Slope For Each Year's Horizontal Break and Stuff+ Linear Model
stuff_plus_horizontal <- h_break_stuff_plus_slope |> 
  mutate(ymin = slope - std.error, ymax = slope + std.error) |>
  ggplot() +
  geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") +
  geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) +
  geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) +
  labs(title = "Horizontal Break's Impact on Stuff+",
       x = "Year",
       y = "Change in Stuff+ Per Inch of Horizontal Break") +
  theme + 
  theme(axis.title.y = element_text(size = 10),
        axis.text.x = element_text(size = 10))

# Graph of Slope For Each Year's Horizontal Break and xwOBA Linear Model
xwOBA_horizontal <- h_break_xwOBA_slope |> 
  mutate(ymin = slope - std.error, ymax = slope + std.error) |>
  ggplot() +
  geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") +
  geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) +
  geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) +
  labs(title = "Horizontal Break's Impact on xwOBA",
       x = "Year",
       y = "Change in xwOBA Per Inch of Horizontal Break") +
  theme +
  theme(axis.title.y = element_text(size = 10),
        axis.text.x = element_text(size = 10))

grid.arrange(stuff_plus_horizontal, xwOBA_horizontal, ncol=2)
```

<!-- ## Stuff+ And xwOBAcon -->

<!-- ```{r} -->
<!-- #| fig-width: 12 -->
<!-- #| fig-height: 5 -->
<!-- #| fig.align: 'center' -->

<!-- # Graph of Slope For Each Year's Horizontal Break and Stuff+ Linear Model -->
<!-- stuff_plus_horizontal <- h_break_stuff_plus_slope |>  -->
<!--   mutate(ymin = slope - std.error, ymax = slope + std.error) |> -->
<!--   ggplot() + -->
<!--   geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") + -->
<!--   geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) + -->
<!--   geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) + -->
<!--   labs(title = "Horizontal Break's Impact on Stuff+", -->
<!--        x = "Year", -->
<!--        y = "Change in Stuff+ Per Inch of Horizontal Break") + -->
<!--   theme +  -->
<!--   theme(axis.title.y = element_text(size = 10), -->
<!--         axis.text.x = element_text(size = 10)) -->

<!-- # Graph of Slope For Each Year's Horizontal Break and xwOBA Linear Model -->
<!-- xwOBAcon_horizontal <- h_break_wOBAcon_slope |>  -->
<!--   mutate(ymin = slope - std.error, ymax = slope + std.error) |> -->
<!--   ggplot() + -->
<!--   geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") + -->
<!--   geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) + -->
<!--   geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) + -->
<!--   labs(title = "Horizontal Break's Impact on wOBAcon", -->
<!--        x = "Year", -->
<!--        y = "Change in wOBAcon Per Inch of Horizontal Break") + -->
<!--   theme + -->
<!--   theme(axis.title.y = element_text(size = 10), -->
<!--         axis.text.x = element_text(size = 10)) -->

<!-- grid.arrange(stuff_plus_horizontal, xwOBAcon_horizontal, ncol=2) -->
<!-- ``` -->

## Stuff+ And Whiff Percentage 
```{r}
#| fig-width: 12
#| fig-height: 5
#| fig.align: 'center'

# Graph of Slope For Each Year's Horizontal Break and Whiff Percentage Linear Model
whiff_horizontal <- h_break_whiff_slope |> 
  mutate(ymin = slope - std.error, ymax = slope + std.error) |>
  ggplot() +
  geom_line(mapping = aes(x = season, y = slope), size = 1, group = 1, color = "red") +
  geom_point(mapping = aes(x = season, y = slope), color = "black", size = 2) +
  geom_errorbar(mapping = aes(x = season, ymin = ymin, ymax = ymax), width = 0.2, position = position_dodge(0.05)) +
  labs(title = "Horizontal Break's Impact on Whiff%",
       x = "Year",
       y = "Change in Whiff% Per Inch of Horizontal Break") +
  theme +
  theme(axis.title.y = element_text(size = 10),
        axis.text.x = element_text(size = 10))

grid.arrange(stuff_plus_horizontal, whiff_horizontal, ncol=2)
```

