---
title: "Main doc"
author: "Belle Schmidt"
date: "2024-06-24"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

### Libraries

```{r}
library(tidyverse)
library(ggridges)
library(ggthemes)
library(pillar)
library(baseballr)
library(readr)
library(viridis)
```

### Read Statcast Dataset

```{r}

Statcast_Combined_Pitches <- read.csv("StatcastCombinedPitches.csv")

Joined_FanGraphs_Statcast <- read.csv("Joined_FanGraphs_Statcast.csv")

PitchUse <- read.csv("PitchUse.csv")

```




### The Proportion Each Pitch Type Was Thrown Each Year

```{r}
# Use of Each Fastpitch Per Year
fastball_frequency_graph <- PitchUse |> 
  filter(pitch_name %in% c("4-Seam Fastball", "Cutter", "Sinker")) |> 
ggplot(aes(x = year, y = prop, fill = year)) +
  geom_bar(stat = "identity") +
  facet_wrap(~pitch_name) +
  labs(title = "Use of Each Fastball Type Per Year",
       x = "Year",
       y = "Proportion") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 11),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white"))

fastball_frequency_graph

# Use of Each Offspeed Per Year
offspeed_frequency_graph <- PitchUse |> 
  filter(pitch_name %in% c("Changeup", "Forkball", "Knuckle Curve", "Split-Finger")) |> 
ggplot(aes(x = year, y = prop, fill = year)) +
  geom_bar(stat = "identity") +
  facet_wrap(~pitch_name) +
   labs(title = "Use of Each Offspeed Type Per Year",
       x = "Year",
       y = "Proportion") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour= "black"),
strip.text.x = element_text(color = "white"))

offspeed_frequency_graph

# Use of Each Breaking Ball Per Year
BreakingBall_frequency_graph <- PitchUse |> 
  filter(pitch_name %in% c("Curveball", "Knuckleball", "Slider")) |> 
ggplot(aes(x = year, y = prop, fill = year)) +
  geom_bar(stat = "identity") +
  facet_wrap(~pitch_name) +
   labs(title = "Use of Each Breaking Ball Type Per Year",
       x = "Year",
       y = "Proportion") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
         axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white"))

BreakingBall_frequency_graph
```


# WOBA Distribution For Each Pitch Type (Without Combining Pitches)

```{r}


fastball_WOBA <- WOBA |> 
  filter(pitch_name %in% c("4-Seam Fastball", "Cutter", "Sinker")) |> 
  ggplot(aes(x = woba_value, y = year, fill = year)) +
  geom_density_ridges(scale = 0.9) +
  facet_wrap(~pitch_name) +
  coord_cartesian(xlim = c(0, 2)) +
  labs(title = "WOBA Distribution For All Types of Fastballs Per Year",
       x = "WOBA Value",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) +
  scale_fill_colorblind()

fastball_WOBA

offspeed_WOBA <- WOBA |> 
  filter(pitch_name %in% c("Changeup", "Forkball", "Knuckle Curve", "Screwball", "Split-Finger")) |>
  ggplot(aes(x = woba_value, y = year, fill = year)) +
  geom_density_ridges(scale = 0.9) +
  facet_wrap(~pitch_name) +
  coord_cartesian(xlim = c(0, 2)) +
  labs(title = "WOBA Distribution For All Types of Offspeed Pitches Per Year",
       x = "WOBA Value",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) +
  scale_fill_colorblind()

offspeed_WOBA 

BreakingBall_WOBA <- WOBA |> 
  filter(pitch_name %in% c("Curveball", "Knuckleball", "Slider", "Slurve", "Sweeper", "Slow Curve")) |> 
  ggplot(aes(x = woba_value, y = year, fill = year)) +
  geom_density_ridges(scale = 0.7) +
  facet_wrap(~pitch_name) +
  coord_cartesian(xlim = c(0, 2)) +
  labs(title = "WOBA Distribution For All Types of Breaking Balls Per Year",
       x = "WOBA Value",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 1.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) +
  scale_fill_colorblind()

BreakingBall_WOBA  
```


### WOBA By Individual Pitch Type (Not Combined)

```{r}
# WOBA Distribution of 4-Seam Fastball
FourSeamFastball_WOBA <- WOBA |> 
  filter(pitch_name == "4-Seam Fastball") |> 
  ggplot(aes(x = woba_value, y = year, fill = year)) +
  geom_density_ridges(scale = 0.9) +
  coord_cartesian(xlim = c(0, 2)) +
  labs(title = "WOBA Distribution For 4-Seam Fastballs Per Year",
       x = "WOBA Value",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold")) +
  scale_fill_colorblind()

FourSeamFastball_WOBA

# WOBA Distribution of Cutter
Cutter_WOBA <- WOBA |> 
  filter(pitch_name == "Cutter") |> 
  ggplot(aes(x = woba_value, y = year, fill = year)) +
  geom_density_ridges(scale = 0.9) +
  coord_cartesian(xlim = c(0, 2)) +
  labs(title = "WOBA Distribution For Cutters Per Year",
       x = "WOBA Value",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold")) +
  scale_fill_colorblind()

Cutter_WOBA

# WOBA Distribution of Sinker
Sinker_WOBA <- WOBA |> 
  filter(pitch_name == "Sinker") |> 
  ggplot(aes(x = woba_value, y = year, fill = year)) +
  geom_density_ridges(scale = 0.9) +
  coord_cartesian(xlim = c(0, 2)) +
  labs(title = "WOBA Distribution For Sinkers Per Year",
       x = "WOBA Value",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold")) +
  scale_fill_colorblind()

Sinker_WOBA

# WOBA Distribution of Change Up
ChangeUp_WOBA <- WOBA |> 
  filter(pitch_name == "Changeup") |> 
  ggplot(aes(x = woba_value, y = year, fill = year)) +
  geom_density_ridges(scale = 0.9) +
  coord_cartesian(xlim = c(0, 2)) +
  labs(title = "WOBA Distribution For Changeups Per Year",
       x = "WOBA Value",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold")) +
  scale_fill_colorblind()

ChangeUp_WOBA

# WOBA Distribution of Forkball
Forkball_WOBA <- WOBA |> 
  filter(pitch_name == "Forkball") |> 
  ggplot(aes(x = woba_value, y = year, fill = year)) +
  geom_density_ridges(scale = 0.9) +
  coord_cartesian(xlim = c(0, 2)) +
  labs(title = "WOBA Distribution For Forkballs Per Year",
       x = "WOBA Value",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold")) +
  scale_fill_colorblind()

Forkball_WOBA

# WOBA Distribution of Knuckle Curve
KnuckleCurve_WOBA <- WOBA |> 
  filter(pitch_name == "Knuckle Curve") |> 
  ggplot(aes(x = woba_value, y = year, fill = year)) +
  geom_density_ridges(scale = 0.9) +
  coord_cartesian(xlim = c(0, 2)) +
  labs(title = "WOBA Distribution For Knuckle Curves Per Year",
       x = "WOBA Value",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold")) +
  scale_fill_colorblind()

KnuckleCurve_WOBA

# WOBA Distribution of Screwball
Screwball_WOBA <- WOBA |> 
  filter(pitch_name == "Screwball") |> 
  ggplot(aes(x = woba_value, y = year, fill = year)) +
  geom_density_ridges(scale = 0.9) +
  coord_cartesian(xlim = c(0, 2)) +
  labs(title = "WOBA Distribution For Screwballs Per Year",
       x = "WOBA Value",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold")) +
  scale_fill_colorblind()

Screwball_WOBA

# WOBA Distribution of Split-Finger
SplitFinger_WOBA <- WOBA |> 
  filter(pitch_name == "Split-Finger") |> 
  ggplot(aes(x = woba_value, y = year, fill = year)) +
  geom_density_ridges(scale = 0.9) +
  coord_cartesian(xlim = c(0, 2)) +
  labs(title = "WOBA Distribution For Split-Fingers Per Year",
       x = "WOBA Value",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold")) +
  scale_fill_colorblind()

SplitFinger_WOBA

# WOBA Distribution of Curveball
Curveball_WOBA <- WOBA |> 
  filter(pitch_name == "Curveball") |> 
  ggplot(aes(x = woba_value, y = year, fill = year)) +
  geom_density_ridges(scale = 0.9) +
  coord_cartesian(xlim = c(0, 2)) +
  labs(title = "WOBA Distribution For Curveballs Per Year",
       x = "WOBA Value",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold")) +
  scale_fill_colorblind()

Curveball_WOBA

# WOBA Distribution of Knuckle ball
Knuckleball_WOBA <- WOBA |> 
  filter(pitch_name == "Knuckleball") |> 
  ggplot(aes(x = woba_value, y = year, fill = year)) +
  geom_density_ridges(scale = 0.9) +
  coord_cartesian(xlim = c(0, 2)) +
  labs(title = "WOBA Distribution For Knuckleballs Per Year",
       x = "WOBA Value",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold")) +
  scale_fill_colorblind()

Knuckleball_WOBA

# WOBA Distribution of Curveball
Slider_WOBA <- WOBA_Combined |> 
  filter(pitch_name == "Slider") |> 
  ggplot(aes(x = woba_value, y = year, fill = year)) +
  geom_density_ridges(scale = 0.9) +
  coord_cartesian(xlim = c(0, 2)) +
  labs(title = "WOBA Distribution For Sliders Per Year",
       x = "WOBA Value",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold")) +
  scale_fill_colorblind()

Slider_WOBA

# WOBA Distribution of Slow Curves
SlowCurve_WOBA <- WOBA |> 
  filter(pitch_name == "Slow Curve") |> 
  ggplot(aes(x = woba_value, y = year, fill = year)) +
  geom_density_ridges(scale = 0.9) +
  coord_cartesian(xlim = c(0, 2)) +
  labs(title = "WOBA Distribution For Slow Curves Per Year",
       x = "WOBA Value",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold")) +
  scale_fill_colorblind()

SlowCurve_WOBA

# WOBA Distribution of Slurves
Slurve_WOBA <- WOBA |> 
  filter(pitch_name == "Slurve") |> 
  ggplot(aes(x = woba_value, y = year, fill = year)) +
  geom_density_ridges(scale = 0.9) +
  coord_cartesian(xlim = c(0, 2)) +
  labs(title = "WOBA Distribution For Slurves Per Year",
       x = "WOBA Value",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold")) +
  scale_fill_colorblind()

Slurve_WOBA

# WOBA Distribution of Sweepers
Sweeper_WOBA <- WOBA |> 
  filter(pitch_name == "Sweeper") |> 
  ggplot(aes(x = woba_value, y = year, fill = year)) +
  geom_density_ridges(scale = 0.9) +
  coord_cartesian(xlim = c(0, 2)) +
  labs(title = "WOBA Distribution For Sweepers Per Year",
       x = "WOBA Value",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold")) +
  scale_fill_colorblind()

Sweeper_WOBA
```

### WOBA By Individual Pitch Type (Combined)

```{r}

# WOBA Distribution of Curveball
Curveball_WOBA <- WOBA_Combined |> 
  filter(pitch_name == "Curveball") |> 
  ggplot(aes(x = woba_value, y = year, fill = year)) +
  geom_density_ridges(scale = 0.9) +
  coord_cartesian(xlim = c(0, 2)) +
  labs(title = "WOBA Distribution For Curveballs Per Year",
       x = "WOBA Value",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold")) +
  scale_fill_colorblind()

Curveball_WOBA

# WOBA Distribution of Curveball
Slider_WOBA <- WOBA_Combined |> 
  filter(pitch_name == "Slider") |> 
  ggplot(aes(x = woba_value, y = year, fill = year)) +
  geom_density_ridges(scale = 0.9) +
  coord_cartesian(xlim = c(0, 2)) +
  labs(title = "WOBA Distribution For Sliders Per Year",
       x = "WOBA Value",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold")) +
  scale_fill_colorblind()

Slider_WOBA
```


### Relationship Between Change in Run Expectancy and Velocity (Pitch-By-Pitch)

```{r}
# Run Value For Each Pitch Based on Velocity
Statcast_Combined_Pitches |> 
  ggplot(aes(x = release_speed, y = delta_run_exp,
             color = pitch_name, alpha = .2)) +
  geom_point() +
  facet_wrap(~pitch_name)
```

```{r}
# Run Value For Each Pitch Based on Velocity For Each Year - Scatter Plot
Joined_FanGraphs_Statcast |> 
  ggplot(aes(x = avg_velocity_FF, y = run_value_per100_FF, color = Season)) +
  geom_point(alpha = .3) +
  facet_wrap(~Season) +
  labs(title = "Pitcher's Average Fastball Velocity Corresponding to Run Value Per 100 Pitches",
       x = "Pitcher's Average Velocity",
       y = "Pitcher's Run Value Per 100 Pitches") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold"),
        strip.text = element_text(face = "bold", size = 12,lineheight = 3.0),
strip.background = element_rect(fill = "steelblue4", colour = "black"),
strip.text.x = element_text(color = "white")) 
```

```{r}
# Run Value For Each Pitch Based on Velocity For Each Year - Scatter Plot
Statcast |> 
  filter(pitch_name == "4-Seam Fastball") |> 
  mutate(year = as.character(year)) |> 
  ggplot(aes(x = release_speed, y = delta_run_exp,
             color = year)) +
  geom_point(alpha = .2)
```

```{r}
# Change in Run Value Based on Velocity - Bins

Statcast |> 
  filter(pitch_name != "", pitch_name != "Eephus", pitch_name != "Other", pitch_name != "Pitch Out") |> 
  ggplot(aes(x = release_speed, y = delta_run_exp,
             color = pitch_name)) +
  stat_bin_2d(bins = 60, colour = "white")
```


```{r}
# Change in Run Value For Fastballs Of Various Velocities in 2020
Statcast |> 
  filter(pitch_name == "4-Seam Fastball", year == "2020") |> 
  ggplot(aes(x = release_speed, y = delta_run_exp,
             color = pitch_name)) +
  stat_bin_2d(bins = 45, colour = "white") +
   scale_x_continuous(limits = c(70, 105))

# Change in Run Value For Fastballs Of Various Velocities in 2021
Statcast |> 
  filter(pitch_name == "4-Seam Fastball", year == "2021") |> 
  ggplot(aes(x = release_speed, y = delta_run_exp,
             color = pitch_name)) +
  stat_bin_2d(bins = 45, colour = "white") +
  scale_x_continuous(limits = c(70, 105))

# Change in Run Value For Fastballs Of Various Velocities in 2022
Statcast |> 
  filter(pitch_name == "4-Seam Fastball", year == "2022") |> 
  ggplot(aes(x = release_speed, y = delta_run_exp,
             color = pitch_name)) +
  stat_bin_2d(bins = 45, colour = "white") +
  scale_x_continuous(limits = c(70, 105))

# Change in Run Value For Fastballs Of Various Velocities in 2023
Statcast |> 
  filter(pitch_name == "4-Seam Fastball", year == "2023") |> 
  ggplot(aes(x = release_speed, y = delta_run_exp,
             color = pitch_name)) +
  stat_bin_2d(bins = 45, colour = "white") +
  scale_x_continuous(limits = c(70, 105))

# Change in Run Value For Fastballs Of Various Velocities in 2023
Statcast |> 
  filter(pitch_name == "4-Seam Fastball", year == 2024) |> 
  ggplot(aes(x = release_speed, y = delta_run_exp,
             color = pitch_name)) +
  stat_bin_2d(bins = 45, colour = "white") +
  scale_x_continuous(limits = c(70, 105))
```


```{r}
# Change in Run Value For Cutters Of Various Velocities
Statcast |> 
  filter(pitch_name == "Cutter") |> 
  ggplot(aes(x = release_speed, y = delta_run_exp,
             color = pitch_name)) +
  stat_bin_2d(bins = 35, colour = "white")
```

```{r}
# Change in Run Value For Sinkers Of Various Velocities
Statcast |> 
  filter(pitch_name == "Sinker") |> 
  ggplot(aes(x = release_speed, y = delta_run_exp,
             color = pitch_name)) +
  stat_bin_2d(bins = 35, colour = "white")
```

```{r}
# Change in Run Value For Change-Ups Of Various Velocities
Statcast |> 
  filter(pitch_name == "Changeup") |> 
  ggplot(aes(x = release_speed, y = delta_run_exp,
             color = pitch_name)) +
  stat_bin_2d(bins = 50, colour = "white")
```

```{r}
# Random Plot To Determine Quantity of times something occurred 
ggplot(Statcast, aes(x = release_speed, delta_run_exp)) +
  geom_raster() +
  scale_fill_viridis() 
```

```{r}
# Density Plot of Run Value Per 100 Pitches Per Season For 4-Seam Fastballs

FourSeamFastball <- Joined_FanGraphs_Statcast |> 
  mutate(Season = as.character(Season)) |> 
  ggplot(aes(x = run_value_per100_FF, y = Season, fill = Season)) +
  geom_density_ridges(scale = 0.9) +
  labs(title = "Run Value Per 100 Pitches Distribution For 4-Seam Fastballs",
       x = "Run Value Per 100 Pitches",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold")) +
  scale_fill_colorblind() +
  coord_cartesian(xlim = c(-25, 25)) 

FourSeamFastball
```

```{r}
# Density Plot of Run Value Per 100 Pitches Per Season For Change Ups

Change_Up <- Joined_FanGraphs_Statcast |> 
  mutate(Season = as.character(Season)) |> 
  ggplot(aes(x = run_value_per100_CH, y = Season, fill = Season)) +
  geom_density_ridges(scale = 0.9) +
  labs(title = "Run Value Per 100 Pitches Distribution For Change Ups",
       x = "Run Value Per 100 Pitches",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold")) +
  scale_fill_colorblind() +
  coord_cartesian(xlim = c(-25, 25)) 

Change_Up
```

```{r}
# Density Plot of Run Value Per 100 Pitches Per Season For Cutters

Cutters <- Joined_FanGraphs_Statcast |> 
  mutate(Season = as.character(Season)) |> 
  ggplot(aes(x = run_value_per100_FC, y = Season, fill = Season)) +
  geom_density_ridges(scale = 0.9) +
  labs(title = "Run Value Per 100 Pitches Distribution For Cutters",
       x = "Run Value Per 100 Pitches",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold")) +
  scale_fill_colorblind() +
  coord_cartesian(xlim = c(-25, 25)) 

Cutters
```


```{r}
# Density Plot of Run Value Per 100 Pitches Per Season For Sliders

Slider <- Joined_FanGraphs_Statcast |> 
  mutate(Season = as.character(Season)) |> 
  ggplot(aes(x = run_value_per100_SL, y = Season, fill = Season)) +
  geom_density_ridges(scale = 0.9) +
  labs(title = "Run Value Per 100 Pitches Distribution For Sliders",
       x = "Run Value Per 100 Pitches",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold")) +
  scale_fill_colorblind() +
  coord_cartesian(xlim = c(-25, 25)) 

Slider
```


```{r}
# Density Plot of Run Value Per 100 Pitches Per Season For Knuckle Curves

Knuckle_Curve <- Joined_FanGraphs_Statcast |> 
  mutate(Season = as.character(Season)) |> 
  ggplot(aes(x = run_value_per100_KC, y = Season, fill = Season)) +
  geom_density_ridges(scale = 0.9) +
  labs(title = "Run Value Per 100 Pitches Distribution For Knuckle Curves",
       x = "Run Value Per 100 Pitches",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold")) +
  scale_fill_colorblind() +
  coord_cartesian(xlim = c(-25, 25)) 

Knuckle_Curve
```

```{r}
# Density Plot of Run Value Per 100 Pitches Per Season For Curves

Curve <- Joined_FanGraphs_Statcast |> 
  mutate(Season = as.character(Season)) |> 
  ggplot(aes(x = run_value_per100_CU, y = Season, fill = Season)) +
  geom_density_ridges(scale = 0.9) +
  labs(title = "Run Value Per 100 Pitches Distribution For Curves",
       x = "Run Value Per 100 Pitches",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold")) +
  scale_fill_colorblind() +
  coord_cartesian(xlim = c(-25, 25)) 

Curve
```


```{r}
# Density Plot of Run Value Per 100 Pitches Per Season For Sinkers

Sinkers <- Joined_FanGraphs_Statcast |> 
  mutate(Season = as.character(Season)) |> 
  ggplot(aes(x = run_value_per100_SI, y = Season, fill = Season)) +
  geom_density_ridges(scale = 0.9) +
  labs(title = "Run Value Per 100 Pitches Distribution For Sinkers",
       x = "Run Value Per 100 Pitches",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold")) +
  scale_fill_colorblind() +
  coord_cartesian(xlim = c(-25, 25)) 

Sinkers
```

```{r}
# Density Plot of Run Value Per 100 Pitches Per Season For Splitters
Splitter <- Joined_FanGraphs_Statcast |> 
  mutate(Season = as.character(Season)) |> 
  ggplot(aes(x = run_value_per100_FS, y = Season, fill = Season)) +
  geom_density_ridges(scale = 0.9) +
  coord_cartesian(xlim = c(-25, 25)) +
  labs(title = "Run Value Per 100 Pitches Distribution For Splitters",
       x = "Run Value Per 100 Pitches",
       y = "Year") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title = element_text(face = "bold", size = 12),
        axis.text = element_text(face = "bold")) +
  scale_fill_colorblind()

Splitter
```


### Relationship Between Average Velocity And Run Value Per 100 Pitches

```{r}
# Change in Run Value For Fastballs Of Various Velocities in 2020
Joined_FanGraphs_Statcast |> 
  ggplot(aes(x = avg_velocity_FF, y = run_value_per100_FF)) +
  geom_point(aes(color = Season), alpha = .3) +
  facet_wrap(~Season)
```


```{r}
# Change in Run Value For Change Ups Of Various Velocities in 2020
Joined_FanGraphs_Statcast |> 
  ggplot(aes(x = avg_velocity_CH, y = run_value_per100_CH)) +
  geom_point(aes(color = Season), alpha = .3) +
  coord_cartesian(ylim = c(-25, 25)) +
  facet_wrap(~Season)
```


```{r}
# Change in Run Value For Slider Of Various Velocities in 2020
Joined_FanGraphs_Statcast |> 
  ggplot(aes(x = avg_velocity_SL, y = run_value_per100_SL)) +
  geom_point(aes(color = Season), alpha = .3) +
  coord_cartesian(ylim = c(-25, 25)) +
  facet_wrap(~Season)
```

```{r}
# Change in Run Value For Knuckle Curves Of Various Velocities in 2020
Joined_FanGraphs_Statcast |> 
  ggplot(aes(x = avg_velocity_KC, y = run_value_per100_KC)) +
  geom_point(aes(color = Season), alpha = .3) +
  coord_cartesian(ylim = c(-25, 25)) +
  facet_wrap(~Season)
```

```{r}
# Change in Run Value For Cutters Of Various Velocities in 2020
Joined_FanGraphs_Statcast |> 
  ggplot(aes(x = avg_velocity_FC, y = run_value_per100_FC)) +
  geom_point(aes(color = Season), alpha = .3) +
  coord_cartesian(ylim = c(-25, 25)) +
  facet_wrap(~Season)
```

```{r}
# Change in Run Value For Curves Of Various Velocities in 2020
Joined_FanGraphs_Statcast |> 
  ggplot(aes(x = avg_velocity_CU, y = run_value_per100_CU)) +
  geom_point(aes(color = Season), alpha = .3) +
  coord_cartesian(ylim = c(-25, 25)) +
  facet_wrap(~Season)
```


### Relationship between run Value Per 100 and Stuff+


```{r}
# Run Values Impact on Stuff+ 

Joined_FanGraphs_Statcast |> 
  ggplot(aes(x = run_value_per100_FF, y = stuff_plus_stuff_FF)) +
  geom_point(aes(color = Season), alpha = .3) +
  coord_cartesian(xlim = c(-25, 25)) +
  facet_wrap(~Season)
```


```{r}
# Run Values Impact on Stuff+ 

Joined_FanGraphs_Statcast |> 
  ggplot(aes(x = run_value_per100_FF, y = stuff_plus_stuff_FF)) +
  geom_point(aes(color = Season), alpha = .3) +
  coord_cartesian(xlim = c(-25, 25)) +
  facet_wrap(~Season)
```


```{r}

Joined_FanGraphs_Statcast |> 
  ggplot(aes(x = run_value_per100_CH, y = stuff_plus_stuff_CH)) +
  geom_point(aes(color = Season), alpha = .3) +
  coord_cartesian(xlim = c(-25, 25)) +
  facet_wrap(~Season)
```


```{r}
# Change in Run Value For Slider Of Various Velocities in 2020
Joined_FanGraphs_Statcast |> 
  ggplot(aes(x = run_value_per100_SL, y = stuff_plus_stuff_SL)) +
  geom_point(aes(color = Season), alpha = .3) +
  coord_cartesian(xlim = c(-25, 25)) +
  facet_wrap(~Season)
```

```{r}
# Change in Run Value For Knuckle Curves Of Various Velocities in 2020
Joined_FanGraphs_Statcast |> 
  ggplot(aes(x = run_value_per100_KC, y = stuff_plus_stuff_KC)) +
  geom_point(aes(color = Season), alpha = .3) +
  coord_cartesian(xlim = c(-25, 25)) +
  facet_wrap(~Season)
```

```{r}
# Change in Run Value For Cutters Of Various Velocities in 2020
Joined_FanGraphs_Statcast |> 
  ggplot(aes(x = run_value_per100_FC, y = stuff_plus_stuff_FC)) +
  geom_point(aes(color = Season), alpha = .3) +
  coord_cartesian(xlim = c(-25, 25)) +
  facet_wrap(~Season)
```

```{r}
# Change in Run Value For Curves Of Various Velocities in 2020
Joined_FanGraphs_Statcast |> 
  ggplot(aes(x = run_value_per100_CU, y = stuff_plus_stuff_CU)) +
  geom_point(aes(color = Season), alpha = .3) +
  coord_cartesian(xlim = c(-25, 25)) +
  facet_wrap(~Season)
```


