---
title: "Whiff Percentage Modeling"
author: "Belle Schmidt"
date: "2024-07-18"
output: html_document
---

### Whiff Percentage Modeling

# Libraries
```{r}
library(tidyverse)
library(ranger) # faster implementation of randomforest library
library(vip) # variable importance
library(pdp) # partial dependence plot
library(caret) # train random forest model with cross validation
library(broom) # tidy extract linear summary
```

# Setting the Theme
```{r}
theme_set(theme_bw())
```

# Data
```{r}
pitching_models <- read.csv("mlb_pitching_stats_2020-24.csv")
```


## Cleaning the Data
```{r}
ff_models <- pitching_models |> 
  filter(
    pitch_name == "4-Seam Fastball" &
    !is.na(stuff_plus) & 
    season == 2021
      ) |> 
  mutate(horizontal_break = -horizontal_break) |> 
  select(spin, velocity, extension:horizontal_break, stuff_plus, xwOBA, whiff_pct)
```


## Build Random Forest to Predict Stuff+ for 2021 Season
```{r}
### set seed
set.seed(0829)

### fit model
sp_rf <- ranger(
  stuff_plus ~  . - xwOBA - whiff_pct,
  num.trees = 1000,
  importance = "impurity",
  mtry = 5 / 3,
  data = ff_models
)


### model summary
sp_rf
```

### Variable Importance
```{r}
sp_rf |> 
  vip(
    aesthetics = list(color = "black", 
                      fill = "steelblue4")
  )
```

# Random Forest with 5-fold CV
### fit model
```{r}
sp_rf_cv <- train(
  stuff_plus ~ . - xwOBA - whiff_pct,
  tuneLength = 3,
  data = ff_models,
  method = "ranger",
  trControl = trainControl(
    method = "cv",
    number = 5,
    verboseIter = TRUE
  )
)

### plot model
plot(sp_rf_cv)


### try tuneGrid
tuneGrid <- data.frame(
  .mtry = c(2, 3, 4, 5),
  .splitrule = "variance",
  .min.node.size = 5
)

### fit model again
sp_rf_cv <- train(
  stuff_plus ~  . - xwOBA - whiff_pct,
  tuneGrid = tuneGrid,
  data = ff_models,
  method = "ranger",
  trControl = trainControl(
    method = "cv",
    number = 5,
    verboseIter = TRUE
  )
)

### model summary
sp_rf_cv


### plot model
plot(sp_rf_cv)
```

# Final Model
```{r}
### set seed
set.seed(0829)

### fit model
sp_rf_final <- ranger(
  stuff_plus ~  . - xwOBA - whiff_pct,
  num.trees = 1000,
  importance = "impurity",
  mtry = 2,
  splitrule = "variance",
  min.node.size = 5,
  data = ff_models
)

### model summary
sp_rf_final
```

# Apply Predictions to the Dataset
```{r}
ff_models <- ff_models |> 
  mutate(pred = sp_rf_final$predictions)
```

# Plot Predictions vs. Original Observed Values
```{r}
ff_models |> 
  ggplot(aes(stuff_plus, pred)) +
  geom_point(alpha = 0.5) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "firebrick1")
```

### Linear Regression to Predict Whiff Percentage
```{r}
### plot whiff percentage by predicted stuff+
ff_models |> 
  ggplot(aes(pred, whiff_pct))+
  geom_point(alpha = 0.5) +
  geom_vline(xintercept = 100, linetype = "dashed", color = "firebrick1")

### plot whiff percentage by stuff+
ff_models |> 
  ggplot(aes(stuff_plus, whiff_pct)) +
  geom_point(alpha = 0.5) +
  geom_vline(xintercept = 100, linetype = "dashed", color = "firebrick1")
```

# Fit Model 
```{r}
whiff_lm <- lm(whiff_pct ~ stuff_plus, data = ff_models)
```

# Model Summary
```{r}
whiff_lm |> 
  tidy()

whiff_lm |> 
  glance()
```

# Normality Check
```{r}
# bin width
bw <-  2 * IQR(ff_models$stuff_plus) / length(ff_models$stuff_plus) ^ (1/3)

# plot
ff_models |> 
  ggplot(aes(stuff_plus)) +
  geom_histogram(fill = "dodgerblue2", color = "grey50", binwidth = bw)


# whiff percentage normality
# bin width
bw <-  2 * IQR(ff_models$whiff_pct) / length(ff_models$whiff_pct) ^ (1/3)

# plot
ff_models |> 
  ggplot(aes(whiff_pct)) +
  geom_histogram(fill = "dodgerblue2", color = "grey50", binwidth = bw)
```


# Plotting Residuals Against Predicted Values
```{r}
 whiff_lm |>
  augment() |>
  ggplot(aes(.fitted, .resid)) +
  geom_point(color = "gray", alpha = 0.75) +
  geom_hline(yintercept = 0, color = "red",
  linetype = "dashed", linewidth = 1.5) +
  geom_smooth(se = FALSE)
```

# Check Assumptions
```{r}
library(ggfortify)
autoplot(whiff_lm, ncol = 4)
```

## Standardized Residuals to Remove Outliers
```{r}
outliers <- whiff_lm |> 
  augment() |> 
  filter(abs(.std.resid) >= 2.6)
```

# Remove points that are outliers, high leverage points, and influential points
```{r}
resid_analysis <- whiff_lm |> 
  augment() |> 
  # remove outliers
  filter(abs(.std.resid) <= 2.6) 
  # remove high leverage points
  # filter(.hat <= 3*(1 + 1) / nrow(ff_models))
```

# Fit model again
```{r}
new_whiff_lm <- lm(whiff_pct ~ stuff_plus, data = resid_analysis)
```

# Model Summary
```{r}
new_whiff_lm |> 
  glance()
```

# Plot
```{r}
resid_analysis |> 
  ggplot(aes(stuff_plus, whiff_pct)) +
  geom_point(alpha = 0.5) +
  geom_vline(xintercept = 100, linetype = "dashed", color = "firebrick1") +
  #geom_smooth(method = "loess") +
  geom_smooth(method = "lm")
```

